---
title: "Exploration simple log-log / EC models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(stargazer)
library(knitr)
library(DT)

load('../output/results_simplified.RData')

# VIFs
vifs_loglog = rbindlist(lapply(results_loglog, function(x) x$vif))
vifs_ec = rbindlist(lapply(results_ec, function(x) x$vif))

# elasticities
elast_loglog = rbindlist(lapply(results_loglog, function(x) x$elast))
elast_ec = rbindlist(lapply(results_ec, function(x) x$elast))

```

The purpose of this document is to explore how well simple models perform in estimating elasticities.
Here, I am showing the results of two models: a simple log-log model in levels with a lagged DV to model dynamics, and an error-correction specification.


# Log-log model

## Example model specification for one brand

Let us first look at the model results for *one* example brand. I've generated this to illustrate the model configuration (i.e., covariates) and dependent variable.

```{r, results = 'asis', echo = FALSE}
stargazer(results_loglog[[1]]$model, type='html')
cat(paste0('Dependent variable: ', colnames(results_loglog[[1]]$model$model)[1]), fill =T)

```

## Summary of elasticities

### by variable type

```{r, echo = FALSE}

tmp = elast_loglog[!is.na(elastlt), list(N=.N,mean=mean(elastlt), min=min(elastlt), max = max(elastlt), sd=sd(elastlt)),by=c('variable')]
kable(tmp)
```

### by category and variable type

```{r, echo = FALSE}

tmp = elast_loglog[!is.na(elastlt), list(N=.N,mean=mean(elastlt), min=min(elastlt), max = max(elastlt), sd=sd(elastlt)),by=c('variable', 'category')]
setorder(tmp,variable, category)

kable(tmp)

```

## Summary of VIFs

### by covariate

```{r, echo = FALSE}

tmp = vifs_loglog[, list(N=.N,mean=mean(vif), min=min(vif), max = max(vif)),by=c('variable')]
setorderv(tmp,'mean', order=-1L)

kable(tmp, caption = 'VIFs, ordered in descending order of mean VIFs')

```

### by category

```{r, echo = FALSE}

tmp = vifs_loglog[, list(N=.N,mean=mean(vif), min=min(vif), max = max(vif)),by=c('category')]
setorderv(tmp,'mean', order=-1L)

kable(tmp, caption = 'VIFs, ordered in descending order of mean VIFs')

```

### for a few example models

```{r, echo  = FALSE, results = 'asis'}
for (bid in c(10,100,1000)) print(kable(vifs_loglog[brand_id==bid], caption = paste0('VIFs for brand_id ', bid)))
```

### VIFs (scrollable table in descending order of VIFs, capped at 1000 entries)

```{r, echo = FALSE}

tmp=vifs_loglog
setorderv(tmp, 'vif',order=-1L)
DT::datatable(head(tmp,1000))
```


### VIFs (scrollable table without product attributes in descending order of VIFs, capped at 1000 entries)

```{r, echo = FALSE}

tmp=vifs_loglog[!grepl('attr[_]', variable)]
setorderv(tmp, 'vif',order=-1L)
DT::datatable(head(tmp,1000))
```


# EC model

## Example model specification for one brand

Let us first look at the model results for *one* example brand. I've generated this to illustrate the model configuration (i.e., covariates) and dependent variable.

```{r, results = 'asis', echo = FALSE}
stargazer(results_ec[[1]]$model, type='html')
cat(paste0('Dependent variable: ', colnames(results_ec[[1]]$model$model)[1]), fill =T)

```

## Summary of elasticities

### by variable type

```{r, echo = FALSE}

tmp = elast_ec[!is.na(elastlt), list(N=.N,mean=mean(elastlt), min=min(elastlt), max = max(elastlt), sd=sd(elastlt)),by=c('variable')]
kable(tmp)
```

### by category and variable type

```{r, echo = FALSE}

tmp = elast_ec[!is.na(elastlt), list(N=.N,mean=mean(elastlt), min=min(elastlt), max = max(elastlt), sd=sd(elastlt)),by=c('variable', 'category')]
setorder(tmp,variable, category)

kable(tmp)

```

## Summary of VIFs

### by covariate

```{r, echo = FALSE}

tmp = vifs_ec[, list(N=.N,mean=mean(vif), min=min(vif), max = max(vif)),by=c('variable')]
setorderv(tmp,'mean', order=-1L)

kable(tmp, caption = 'VIFs, ordered in descending order of mean VIFs')

```

### by category

```{r, echo = FALSE}

tmp = vifs_ec[, list(N=.N,mean=mean(vif), min=min(vif), max = max(vif)),by=c('category')]
setorderv(tmp,'mean', order=-1L)

kable(tmp, caption = 'VIFs, ordered in descending order of mean VIFs')

```

### for a few example models

```{r, echo  = FALSE, results = 'asis'}
for (bid in c(10,100,1000)) print(kable(vifs_ec[brand_id==bid], caption = paste0('VIFs for brand_id ', bid)))
```

### VIFs (scrollable table in descending order of VIFs, capped at 1000 entries)

```{r, echo = FALSE}

tmp=vifs_ec
setorderv(tmp, 'vif',order=-1L)
DT::datatable(head(tmp,1000))
```


### VIFs (scrollable table without product attributes in descending order of VIFs, capped at 1000 entries)

```{r, echo = FALSE}

tmp=vifs_ec[!grepl('attr[_]', variable)]
setorderv(tmp, 'vif',order=-1L)
DT::datatable(head(tmp,1000))
```