---
title: "Simulation of Latent Instrumental Variables"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, echo = FALSE}
set.seed(1234)
```

As a first step towards our own LIV estimation for the GfK project, I propose to code up:

Ebbes, P., Wedel, M., Böckenholt, U., & Steerneman, T. (2005). Solving and testing for regressor-error (in) dependence when no instrumental variables are available: With new evidence for the effect of education on income. *Quantitative Marketing and Economics*, 3(4), 365-392. To the extent possible, I adhere to the notation in that paper.

# 2.0 LIV 

# 2.1 Simulate data

```{r}

sim_data <- function(rho = .5, N = 1000, pi_vals = c(-.3, .7), coef_x = 3) {
  # Number of observations
  #N = 1000
  
  # Coefficients on latent instruments
  #pi_vals = c(-.3, .7) 
  
  # Class probabilities
  p = c(.7, .3)
  
  # Assert the probs sum to 1
  stopifnot(sum(p)==1)
  
  # Number of latent instruments
  k = length(pi_vals)
  
  # Correlation matrix
  R = matrix(c(1, rho,
                  rho, 1), ncol=2)
  # Standard deviations
  S <- c(sqrt(.5), sqrt(.5))
  
  cor2cov <- function(R, S) {
   sweep(sweep(R, 1, S, "*"), 2, S, "*")
  }
  
  Sigma = cor2cov(R, S)
  
  # Draws from the Var-Covar Matrix
  
  library(MASS)
  set.seed(1234)
  errorterm = mvrnorm(n = N, mu = c(0,0), Sigma =Sigma)
  
  cor(errorterm)
  cov(errorterm)
  
  z <- sample(1:k, N, replace = T, prob = p)
  cbind(class = 1:k, frequency = table(z), prob = table(z)/sum(table(z)))
  
  # Simulate data
  x = pi_vals[z] + errorterm[,2]
  
  y = 1 + coef_x * x + errorterm[,1]
  
  return(list(data = data.frame(y, x, z), pi_vals=pi_vals, coef_x = coef_x))


}
```

## 2.2 Estimate using OLS

Bias when `rho = .5`

```{r}
# bias:
out=sim_data(rho = 0.95, coef_x=.5, pi_vals=c(-1,2))
hist(out$data$x, breaks=100)
summary(lm(y~1+x, data = out$data))
```

```{r}
# recovery by package
out=sim_data(rho = .3, coef_x=.5, pi_vals=c(-1,2), N = 10000)
#hist(out$data$x, breaks=100)
#out$data$y = out$data$y
library(REndo)

l <- latentIV(y~x, data = out$data)
summary(l)

```

summary(l)


No bias when `rho = 0`

```{r}
# no bias:
out=sim_data(rho = 0, coef_x=.5, pi_vals=c(-1,2))
summary(lm(y~1+x, data = out$data))
```

## 2.3 Recovery using MLE a la Ebbes et al. 

### Estimation
```{r}
library(stats4)

# Simulate data
set.seed(999)
out=sim_data(rho = .3, coef_x=.5, pi_vals=c(-1,2), N = 100)
source('liv_llik.R')

y=out$data$y
x=out$data$x
z=out$data$z
pi_vals=out$pi_vals

params = c(0, 1, 1, 0, 1, 0, 1, 2)

MLE = optimx(params, fn = llik, method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE))
unlist(MLE)

llik(params, sim=T)

MLE = optimx(params, fn = llik, method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE), sim=T)
unlist(MLE)


```
