---
title: "Simulation of Latent Instrumental Variables"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, echo = FALSE}
set.seed(1234)
```

As a first step towards our own LIV estimation for the GfK project, I propose to code up:

Ebbes, P., Wedel, M., Böckenholt, U., & Steerneman, T. (2005). Solving and testing for regressor-error (in) dependence when no instrumental variables are available: With new evidence for the effect of education on income. *Quantitative Marketing and Economics*, 3(4), 365-392. To the extent possible, I adhere to the notation in that paper.

# 2.0 LIV 

# 2.1 Simulate data

```{r}

sim_data <- function(rho = .5, N = 1000) {
  # Number of observations
  #N = 1000
  
  # Coefficients on latent instruments
  pi = c(5, 7) 
  
  # Class probabilities
  p = c(.7, .3)
  
  # Assert the probs sum to 1
  stopifnot(sum(p)==1)
  
  # Number of latent instruments
  k = length(pi)
  
  # Correlation matrix
  R = matrix(c(1, rho,
                  rho, 1), ncol=2)
  # Standard deviations
  S <- c(2, 1)
  
  cor2cov <- function(R, S) {
   sweep(sweep(R, 1, S, "*"), 2, S, "*")
  }
  
  Sigma = cor2cov(R, S)
  
  # Draws from the Var-Covar Matrix
  
  library(MASS)
  set.seed(1234)
  errorterm = mvrnorm(n = N, mu = c(0,0), Sigma =Sigma)
  
  cor(errorterm)
  cov(errorterm)
  
  z <- sample(1:k, N, replace = T, prob = p)
  cbind(class = 1:k, frequency = table(z), prob = table(z)/sum(table(z)))
  
  # Simulate data
  x = pi[z] + errorterm[,2]
  
  y = 1 + 3 * x + errorterm[,1]
  
  return(list(data = data.frame(y, x)))

}
```

## 2.2 Estimate using OLS

Bias when `rho = .5`

```{r}
# bias:
out=sim_data(rho = .5)
summary(lm(y~1+x, data = out$data))
```

No bias when `rho = 0`

```{r}
# no bias:
out=sim_data(rho = 0)
summary(lm(y~1+x, data = out$data))
```

## 2.3 Recovery using MLE a la Ebbes et al. 

### Log-likelihood

```{r}

library(mvtnorm)

map_pars <- function(pars) {
  beta0 = pars[1]
  beta1 = pars[2]
  
  # Covariance/correlation structure
  lchol = diag(2)
  lchol[1,1] <- pars[3]
  lchol[2,1] <- pars[4]
  lchol[2,2] <- pars[5]
  
  sigma <- crossprod(lchol)
  
  # class memberships
  prob <- exp(pars[6])/(1+exp(pars[6]))
  
  # instrument coefficients
  lambdas <- double(2)
  lambdas[1] <- pars[7]
  lambdas[2] <- pars[7] + exp(pars[8])
  
  return(list(beta0=beta0, beta1=beta1, lchol=lchol, sigma=sigma, prob=prob, lambdas=lambdas))
}

llik <- function(pars) {
  
  mapped_pars = map_pars(pars)
  beta0 = mapped_pars$beta0
  beta1 = mapped_pars$beta1
  sigma = mapped_pars$sigma
  prob = mapped_pars$prob
  lambdas = mapped_pars$lambdas
  
  # expected values
  x_pred <- prob * lambdas[1] + (1-prob) * lambdas[2] 
  y_pred = beta0 + beta1 * x_pred

  llik = dmvnorm(cbind(y-y_pred, x-x_pred),mean=c(0,0), sigma=sigma, log=T)
  
  return(-sum(llik))
}

```

### Estimation
```{r}
library(stats4)

# Simulate data
set.seed(999)
out=sim_data(rho = .5, N = 10000)
y=out$data$y
x=out$data$x

start_val <- c(1,3,1,1,1, .5, 5, log(2))

# Test log-likelihood function
llik(start_val)

# Determine starting values (y~x)
ols1 <- lm(y~1+x)

start_vals = c(drop(ols1$coefficients)[1], drop(ols1$coefficients)[2], 1, 0, 1, 0, 0,0)

MLE = optim(start_vals, fn = llik,
            method = 'L-BFGS-B',
            lower = .000001)

# recovery is not quite there yet...
map_pars(MLE$par)

```

Correlation is quite extreme

```{r}
# correlation
cov2cor(map_pars(MLE$par)$sigma)
```
