---
title: "Simulation of Latent Instrumental Variables"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, echo = FALSE}
set.seed(1234)
```

As a first step towards our own LIV estimation for the GfK project, I propose to code up:

Ebbes, P., Wedel, M., Böckenholt, U., & Steerneman, T. (2005). Solving and testing for regressor-error (in) dependence when no instrumental variables are available: With new evidence for the effect of education on income. *Quantitative Marketing and Economics*, 3(4), 365-392. To the extent possible, I adhere to the notation in that paper.

# 2.0 LIV 

# 2.1 Simulate data

```{r}

sim_data <- function(rho = .5, N = 1000, pi_vals = c(-.3, .7), coef_x = 3) {
  # Number of observations
  #N = 1000
  
  # Coefficients on latent instruments
  #pi_vals = c(-.3, .7) 
  
  # Class probabilities
  p = c(.7, .3)
  
  # Assert the probs sum to 1
  stopifnot(sum(p)==1)
  
  # Number of latent instruments
  k = length(pi_vals)
  
  # Correlation matrix
  R = matrix(c(1, rho,
                  rho, 1), ncol=2)
  # Standard deviations
  S <- c(sqrt(.5), sqrt(.5))
  
  cor2cov <- function(R, S) {
   sweep(sweep(R, 1, S, "*"), 2, S, "*")
  }
  
  Sigma = cor2cov(R, S)
  
  # Draws from the Var-Covar Matrix
  
  library(MASS)
  set.seed(1234)
  errorterm = mvrnorm(n = N, mu = c(0,0), Sigma =Sigma)
  
  cor(errorterm)
  cov(errorterm)
  
  z <- sample(1:k, N, replace = T, prob = p)
  cbind(class = 1:k, frequency = table(z), prob = table(z)/sum(table(z)))
  
  # Simulate data
  x = pi_vals[z] + errorterm[,2]
  
  y = 1 + coef_x * x + errorterm[,1]
  
  return(list(data = data.frame(y, x, z), pi_vals=pi_vals, coef_x = coef_x))


}
```

## 2.2 Estimate using OLS

Bias when `rho = .5`

```{r}
# bias:
out=sim_data(rho = 0.95, coef_x=.5, pi_vals=c(-1,2))
hist(out$data$x, breaks=100)
summary(lm(y~1+x, data = out$data))
```

```{r}
# recovery by package
out=sim_data(rho = .3, coef_x=.5, pi_vals=c(-1,2), N = 10000)
#hist(out$data$x, breaks=100)
#out$data$y = out$data$y
library(REndo)

l <- latentIV(y~x, data = out$data)
summary(l)

```

summary(l)


No bias when `rho = 0`

```{r}
# no bias:
out=sim_data(rho = 0, coef_x=.5, pi_vals=c(-1,2))
summary(lm(y~1+x, data = out$data))
```

## 2.3 Recovery using MLE a la Ebbes et al. 

### Log-likelihood

```{r}

library(mvtnorm)

map_pars <- function(pars) {
  beta0 = pars[1]
  beta1 = pars[2]
  
  # Covariance/correlation structure
  lchol = diag(2)
  lchol[1,1] <- pars[3]
  lchol[2,1] <- pars[4]
  lchol[2,2] <- pars[5]
  
  sigma <- crossprod(lchol)
  
  # class memberships
  prob <- exp(pars[6])/(1+exp(pars[6]))
  
  # instrument coefficients
  #lambdas <- double(2)
  #lambdas[1] <- pars[7]
  #lambdas[2] <- pars[7] + exp(pars[8])
  lambdas = pars[7:8]  
  return(list(beta0=beta0, beta1=beta1, lchol=lchol, sigma=sigma, prob=prob, lambdas=lambdas))
}

llik <- function(pars) {
  
  mapped_pars = map_pars(pars)
  beta0 = mapped_pars$beta0
  beta1 = mapped_pars$beta1
  sigma = mapped_pars$sigma
  prob = mapped_pars$prob
  lambdas = mapped_pars$lambdas
  
  # expected values
  #x_pred <- prob * lambdas[1] + (1-prob) * lambdas[2]
  
  #x_pred <- pi_vals[z]
  
  ## Debuggen: take actual values of X instead of expected values; do that for y, too
  # 2) Sparren met Peter over terugschatten van parameters
  
  y_pred1 = beta0 + beta1 * lambdas[1]
  y_pred2 = beta0 + beta1 * lambdas[2]

  #sigma = diag(2)
  
  llik1 = dmvnorm(cbind(y, x),mean=c(y_pred1,lambdas[1]), sigma=sigma, log=T)
  llik2 = dmvnorm(cbind(y, x),mean=c(y_pred2, lambdas[2]), sigma=sigma, log=T)
  
  #llik = dnorm(y-y_pred, log=T)
  #llik1 = dnorm(y-y_pred, log=T)
  #llik2 = dnorm(x-x_pred, log=T)
  max.AB = pmax(log(prob) + llik1, log(1-prob) + llik2)
  
  llik_lse = sum(max.AB + log(prob * exp(llik1 - max.AB) + (1-prob) * exp(llik2-max.AB)))
  #print(-sum(llik))
  return(-llik_lse)
}

```


    mu1 <- matrix(data = c(b00 + a1 * pi1, pi1), nrow = 2, ncol = 1)
    pi2 <- params["pi2"]
    mu2 <- matrix(c(b00 + a1 * pi2, pi2), nrow = 2, ncol = 1)
    log.pdf1 <- dmvnorm(m.data.mvnorm, mean = mu1, sigma = varcov, 
        log = TRUE)
    log.pdf2 <- dmvnorm(m.data.mvnorm, mean = mu2, sigma = varcov, 
        log = TRUE)
    max.AB <- pmax(log(pt) + log.pdf1, log(1 - pt) + log.pdf2)
    logLL.lse <- sum(max.AB + log(pt * exp(log.pdf1 - max.AB) + 
        (1 - pt) * exp(log.pdf2 - max.AB)))
    return(-1 * logLL.lse)
    
    
### Estimation
```{r}
library(stats4)

# Simulate data
set.seed(999)
out=sim_data(rho = .3, coef_x=.5, pi_vals=c(-1,2), N = 10000)
#sim_data(rho = .5, N = 1000, coef_x=.5, pi_vals=c(-1,2))
y=out$data$y
x=out$data$x
z=out$data$z
pi_vals=out$pi_vals

start_val <- c(1,3,1,1,1, .5, 5, log(2))

# Test log-likelihood function
llik(start_val)

# Determine starting values (y~x)
ols1 <- lm(y~1+x)

start_vals = c(drop(ols1$coefficients)[1], drop(ols1$coefficients)[2], 1, 0, 1, -5, 1,2)
#start_vals = rep(-1,8) #c(drop(ols1$coefficients)[1], drop(ols1$coefficients)[2], 1, 0, 1, 0, 0,-10)
library(optimx)
#MLE = optim(start_vals, fn = llik,
 #           method = "Nelder-Mead")

params = c('int' = 0, 'p'=1, 'pi1'=0, 'pi2'=0, 'theta5'=0, 'theta6'=1, 'theta7'=0, 'theta8'=1)
#params = c('int' = 1, 'p'=.6, 'pi1'=0, 'pi2'=2, 'theta5'=.5, 'theta6'=1, 'theta7'=0.5, 'theta8'=1)
REndo:::latentIV_LL(params, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p')


MLE = optimx(params, fn = REndo:::latentIV_LL, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p', method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE))
MLE$p

y=out$data$y
x=out$data$x
MLE = optimx(start_vals, fn = llik, method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE))

start_vals, fn = llik,
 #           method = "Nelder-Mead")

#MLE$par

REndo:::latentIV_LL(MLE$par, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p')


# recovery is not quite there yet...

params = c('int' = 0, 'p'=1, 'pi1'=0, 'pi2'=0, 'theta5'=0, 'theta6'=1, 'theta7'=0, 'theta8'=1)

m.sigma = matrix(c(1,0,0,1), nrow=2,byrow=T)
s2e <- m.sigma[1, 1]
s2v <- m.sigma[2, 2]
sev <- m.sigma[1, 2]
varcov <- matrix(0, 2, 2)
varcov[1, 1] <- a1 * a1 * s2v + 2 * a1 * sev + s2e
varcov[2, 1] <- a1 * s2v + sev
varcov[1, 2] <- varcov[2, 1]
varcov[2, 2] <- s2v
  
varcov=matrix(c(2,1,1,1),ncol=2,byrow=T)

crossprod(chol(varcov))
vc=chol(varcov)


params = c('int' = 0, 'p'=1, 'pi1'=0, 'pi2'=0, 'theta5'=0, 'theta6'=vc[1,1], 'theta7'=vc[1,2], 'theta8'=vc[2,2])

params = c('int' = 0, 'p'=1, 'pi1'=0, 'pi2'=0, 'theta5'=0, 'theta6'=1, 'theta7'=0, 'theta8'=1)

#map_pars(MLE$par)

source('llik_new.R')


MLE = optimx(params, fn = llik, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p', method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE))
MLE$p



MLE2 = optimx(params, fn = REndo:::latentIV_LL, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p', method = 'Nelder-Mead', hessian = TRUE, itnmax = 10000, 
        control = list(trace = 0, dowarn = FALSE))
MLE2$p


#params = c('int' = 1, 'p'=.6, 'pi1'=0, 'pi2'=2, 'theta5'=.5, 'theta6'=1, 'theta7'=0.5, 'theta8'=1)
#REndo:::latentIV_LL(params, m.data.mvnorm = cbind(out$data$y, out$data$x), use.intercept = T, name.intercept='int',name.endo.param='p')


```


```{r}
library(REndo)

latentIV(y~x, data=out$data)



#map_pars(start_vals)
```

Correlation is quite extreme

```{r}
# correlation
cov2cor(map_pars(MLE$par)$sigma)
```
  