---
title: "GfK Singapore - RQs"
output:
  html_document: default
  pdf_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
require(stargazer)
library(knitr)
require(xtable)
require(texreg)
library(sjstats)
library(ggplot2)

options(xtable.comment = FALSE)

elast <- fread('../externals/elast_results_MCI_wlag_wotrend.csv')

tableno<<-0
figureno<<-0
fig<-function(caption) {figureno<<-figureno+1;paste0('Figure ', figureno, ': ', caption)}
tab<-function(caption) {tableno<<-tableno+1;paste0('Table ', tableno, ': ', caption)}
```

# Estimation sample
## Overview

Number of markets: `r length(unique(elast$market_id))`.
Number of brands: `r nrow(elast[, .N, by = c('market_id', 'brand')])`.
Number of unique brands: `r nrow(elast[, .N, by = c('brand')])`.

```{r overview2, echo=FALSE, results='asis'}
tmp = elast[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
print(xtable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data')), scalebox='0.6',type='html',caption.placement='top')
```

```{r brand_activity, echo=FALSE,results='asis'}
tmp=elast[, list(ncountries=length(unique(country))), by = c('brand')]
tmp=data.table(table(tmp$ncountries))
setnames(tmp, c('number of countries', 'brands'))
print(xtable(tmp,caption=tab('Brand activity across countries (estimation data)')),include.rownames=FALSE,type='html',longtable=T,caption.placement='top')

```

## Elasticities
```{r elast_ov, echo = FALSE, results='asis'}
  .vars=c('llen','wpswdst','rwpspr','nov6sh')
	
  zval=1.64
	tmp=elast[!is.na(elast), list(median_elast = median(elast), 
												  w_elast = sum(elast/elast_se)/sum(1/elast_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elast/elast_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elast/elast_se)<zval))/.N, 
												  perc_negative = length(which(elast/elast_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], caption = tab('Short-term elasticities by variable for all brands (significance tested at p<.1 (z >= 1.64).'))
	
  tmp=elast[!is.na(elastlt), list(median_elast = median(elastlt), 
												  w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elastlt/elastlt_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elastlt/elastlt_se)<zval))/.N, 
												  perc_negative = length(which(elastlt/elastlt_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], caption = tab('Long-term elasticities by variable for all brands (significance tested at p<.1 (z >= 1.64).'))
	

```



# Selected sample of global brands

Global brands are brands active in at least three countries.

## Overview

```{r sample_overview, echo=FALSE, results='asis'}

tmp=elast[globalbrand==T, list(ncountries=length(unique(country)), ncategories=length(unique(category))), by = c('brand')]
setorderv(tmp, c('ncountries','ncategories'),order=-1L)
print(xtable(tmp, caption=tab('Overview of selected brands (need to be active in at least three countries)')), type='html',caption.placement='top')

```

## Elasticities for global brands
```{r elast_overall, echo = FALSE, results='asis'}
  .vars=c('llen','wpswdst','rwpspr','nov6sh')
	
  zval=1.64
	tmp=elast[!is.na(elast)&globalbrand==T, list(median_elast = median(elast), 
												  w_elast = sum(elast/elast_se)/sum(1/elast_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elast/elast_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elast/elast_se)<zval))/.N, 
												  perc_negative = length(which(elast/elast_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], caption = tab('Short-term elasticities by variable for global brands (significance tested at p<.1 (z >= 1.64).'))
	
  zval=1.64
	tmp=elast[!is.na(elastlt)&globalbrand==T, list(median_elast = median(elastlt), 
												  w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elastlt/elastlt_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elastlt/elastlt_se)<zval))/.N, 
												  perc_negative = length(which(elastlt/elastlt_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], caption = tab('Long-term elasticities by variable for global brands (significance tested at p<.1 (z >= 1.64).'))
	
```

# Research questions

# RQ1: Are marketing elasticities really different in EMs versus developed markets?

## Simple t-tests

```{r rq1, echo = FALSE}
### ANALYSIS 1: elasticities different in high versus low

t_tests <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    # st
    tmpdat[, metric:=elast]
    st=t.test(tmpdat[country_class=='hinc']$metric, tmpdat[country_class=='linc']$metric)
    #lt
    tmpdat[, metric:=elastlt]
    lt=t.test(tmpdat[country_class=='hinc']$metric, tmpdat[country_class=='linc']$metric)
    
    tabl = rbind(data.frame(var=var, type='shortterm', mean1=st$estimate[1], mean2=st$estimate[2], t=st$statistic, p=st$p.value),
                 data.frame(var=var, type='longterm', mean1=lt$estimate[1], mean2=lt$estimate[2], t=lt$statistic, p=lt$p.value))
                 
    
    return(list(summary=tabl, st=st, lt=lt))
})

out=rbindlist(lapply(t_tests, function(x) x$summary))
setnames(out, 'mean1', 'high-income')
setnames(out, 'mean2', 'low-income')

kable(out[type=='shortterm'], caption = tab('T-tests on differences in short-term elasticities between high-income and low-income countries'))

kable(out[type=='longterm'], caption = tab('T-tests on differences in long-term elasticities between high-income and low-income countries'))

```

## Regression approach

with category- and brand-fixed effects.

```{r rq1_regs, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
    st<-lm(elast~1+I(country_class=='linc') + as.factor(category) + as.factor(brand), data = tmpdat)
    lt<-lm(elastlt~1+I(country_class=='linc') + as.factor(category) + as.factor(brand), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for low-income country dummy (versus high-income), using short-term elasticities; regression with fixed effects for countries and brands'))
kable(out[type=='longterm'], caption = tab('Regression estimate for low-income country dummy (versus high-income), using long-term elasticities; regression with fixed effects for countries and brands'))

```

## Regression approach using GDP per capita (instead of dummy)

with category- and brand-fixed effects.

Note that signs reverse, compared to regression before (GDP per capita is reverse-coding for low-income dummy earlier).

```{r rq1_regs_gdp, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
    st<-lm(elast~1+gdppercap + as.factor(category) + as.factor(brand), data = tmpdat)
    lt<-lm(elastlt~1+gdppercap + as.factor(category) + as.factor(brand), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for GDP per capita, using short-term elasticities; regression with fixed effects for countries and brands'))
kable(out[type=='longterm'], caption = tab('Regression estimate for GDP per capita (versus high-income), using long-term elasticities; regression with fixed effects for countries and brands'))

```

# RQ2: Can we assume that marketing mix elasticities are the same within EMs or do they differ across EMs?

Regressing short- and long-term elasticities on country dummies, using brand- and category-fixed effects.
95%-confidence bounds shown (+/- 1.96 * SE).

```{r rq2, echo = FALSE}

regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var&country_class=='linc']
    
      st<-lm(elast~-1+as.factor(country) + as.factor(category) + as.factor(brand), data=tmpdat)
      lt<-lm(elastlt~-1+as.factor(country) + as.factor(category) + as.factor(brand), data=tmpdat)
      
      res=rbindlist(lapply(c('st', 'lt'), function(m) {
        modelname=m
        m=eval(parse(text=m))
        out=data.table(summary(m)$coefficients)
        out[, variable:=rownames(summary(m)$coefficients)]
        setnames(out, c('est', 'se', 't', 'p', 'variable'))
        setcolorder(out, c('variable', 'est', 'se', 't', 'p'))
        out=out[grepl('Intercept|country', variable)]
        out[, variable:=gsub('.*country[)]', '', variable)]
        out[, var:=var]
        out[, type:=modelname]
        return(out)
      }))
      
    return(list(summary=res, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

# boxplot
for (.var in unique(elast$variable)) {
p<-ggplot(out[var==.var], aes(x=variable, y=est, fill=type)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=est-1.96*se, ymax=est+1.96*se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ggtitle(fig(.var))
print(p)
}
```

# R3: When we look at the same markets and product categories, do western brands have the same marketing elasticities than non-western brands?

## Western versus non-western brands

Regressing short- and long-term elasticities on brand-dummy variable (western versus not), using market-level (product-category) fixed effects.

```{r rq3, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
    st<-lm(elast~1+western_brand + as.factor(market_id), data = tmpdat)
    lt<-lm(elastlt~1+western_brand + as.factor(market_id), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for western brand dummy, using short-term elasticities; regression with fixed effects for countries and brands'))
kable(out[type=='longterm'], caption = tab('Regression estimate for western brand dummy, using long-term elasticities; regression with fixed effects for countries and brands'))

```

## Country-of-origin effects

Regressing short- and long-term elasticities on country-of-origin dummies, using brand- and category-fixed effects.
95%-confidence bounds shown (+/- 1.96 * SE).

```{r rq3b, echo = FALSE}

regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
      st<-lm(elast~-1+as.factor(global_country) + as.factor(market_id), data=tmpdat)
      lt<-lm(elastlt~-1+as.factor(global_country) + as.factor(market_id), data=tmpdat)
      
      res=rbindlist(lapply(c('st', 'lt'), function(m) {
        modelname=m
        m=eval(parse(text=m))
        out=data.table(summary(m)$coefficients)
        out[, variable:=rownames(summary(m)$coefficients)]
        setnames(out, c('est', 'se', 't', 'p', 'variable'))
        setcolorder(out, c('variable', 'est', 'se', 't', 'p'))
        out=out[grepl('global[_]country', variable)]
        out[, variable:=gsub('.*country[)]', '', variable)]
        out[, var:=var]
        out[, type:=modelname]
        return(out)
      }))
      
    return(list(summary=res, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

# boxplot
for (.var in unique(elast$variable)) {
p<-ggplot(out[var==.var], aes(x=variable, y=est, fill=type)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=est-1.96*se, ymax=est+1.96*se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))+ggtitle(fig(.var))
print(p)
}
```

## Local versus non-local brands

Regressing short- and long-term elasticities on brand-dummy variable (local to the market, or not), using market-level (product-category) fixed effects.

```{r rq3c, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
    st<-lm(elast~1+local_to_market + as.factor(market_id), data = tmpdat)
    lt<-lm(elastlt~1+local_to_market + as.factor(market_id), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for local-to-market dummy, using short-term elasticities; regression with fixed effects for markets (product/country combinations)'))
kable(out[type=='longterm'], caption = tab('Regression estimate for local-to-market dummy, using long-term elasticities; regression with fixed effects for markets (product/country combinations)'))

```

# RQ4: Are product categories in different life cycle stages across EMs and DMs and what does this imply for marketing mix elasticities? 

## Average growth rates

```{r rq4_growth, echo=FALSE}
tmp=unique(elast, by = c('market_id')) # t-tests on growth rates

t_tests <- lapply(unique(elast$category), function(var) {
    tmpdat = tmp[category == var]
    teststat=t.test(tmpdat[country_class=='hinc']$market_growth, tmpdat[country_class=='linc']$market_growth)
    
    tabl = data.frame(country=var, mean1=teststat$estimate[1], mean2=teststat$estimate[2], t=teststat$statistic, p=teststat$p.value)
                
    return(list(summary=tabl))
})

out=rbindlist(lapply(t_tests, function(x) x$summary))

setnames(out, 'mean1', 'high-income')
setnames(out, 'mean2', 'low-income')

kable(out, caption = tab('Average category growth rates for high-income and low-income countries, and t-test for significance'))

```

## Implications of growth for marketing mix elasticities

regressing short- and long-term elasticities on category growth, with brand-, category-, and country-fixed effects.

```{r rq4b, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[globalbrand==T & variable == var]
    
    st<-lm(elast~1+market_growth + as.factor(brand) + as.factor(category) + as.factor(country), data = tmpdat)
    lt<-lm(elastlt~1+market_growth + as.factor(brand) + as.factor(category) + as.factor(country), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for average category growth, using short-term elasticities; regression with fixed effects for brands, categories, and countries'))
kable(out[type=='longterm'], caption = tab('Regression estimate for average category growth, using long-term elasticities; regression with fixed effects for brands, categories, and countries'))

```

# R5: How does competition from unbranded products affect demand and marketing elasticities in EMs?

I am revising this question: how does competition from local/non-global brands affect marketing elasticities of global brands.

Regressing elasticities on indicator for global brand, with category and country fixed effects.

```{r rq5, echo = FALSE}
regs <- lapply(unique(elast$variable), function(var) {
    tmpdat = elast[variable == var]
    
    st<-lm(elast~1+I(globalbrand==T) + as.factor(category) + as.factor(country), data = tmpdat)
    lt<-lm(elastlt~1+I(globalbrand==T) + as.factor(category) + as.factor(country), data = tmpdat)
    
    tabl = rbind(data.frame(var=var, type='shortterm', coef = summary(st)$coefficients[2,1], p = summary(st)$coefficients[2,4]),
    data.frame(var=var, type='longterm', coef = summary(lt)$coefficients[2,1], p = summary(lt)$coefficients[2,4]))
    
    return(list(summary=tabl, st=st, lt=lt))
})

out = rbindlist(lapply(regs, function(x) x$summary))

kable(out[type=='shortterm'], caption = tab('Regression estimate for global brands (versus local brands), using short-term elasticities; regression with fixed effects for categories, and countries'))
kable(out[type=='longterm'], caption = tab('Regression estimate for global brands, using long-term elasticities; regression with fixed effects for categories, and countries'))

```

#RQ6: What explains most variation in elasticities? Brands, categories, countries?!

