---
title: "GfK Singapore - Results"
output:
  html_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

libs_to_load <- c('data.table', 'stargazer', 'knitr', 'xtable', 'car', 'kableExtra', 'stringi', 'ggplot2', 'ggpubr', 'plyr', 'gridExtra', 'grid', 'lme4', 'sjstats', 'ggthemes') #'blme' 

for (lib in libs_to_load) eval(parse(text=paste('library(', lib, ')')))

options(xtable.comment = FALSE)
options(knitr.kable.NA = '')

# Load data
  brand_panel=fread('../../analysis/temp/preclean.csv')
  brand_panel[, ':=' (date = as.Date(date))]
  
# Load auxilary functions
  source('proc_auxilary.R')
  source('proc_rename.R')

# Preclean data
  elast <- fread('../externals/elast_results_adv.csv') 
  source('preclean.R')
  elast_adv <- copy(elast)

  elast <- fread('../externals/elast_results_novelty.csv') 
  source('preclean.R')
  elast_nov <- copy(elast)

  elast <- fread('../externals/elast_results_firstobs.csv') 
  source('preclean.R')
  elast_firstobs <- copy(elast)
  
  elast <- fread('../externals/elast_results_lastobs.csv') 
  source('preclean.R')
  elast_lastobs <- copy(elast)
    
  elast <- fread('../externals/elast_results_laggedX.csv') 
  source('preclean.R')
  elast_laggedx <- copy(elast)
 
  elast <- fread('../externals/elast_results_simulation.csv') 
  elast[, elastlt:=simelastlt]
  elast[, elastlt_se:=simelastlt_sd]
  elast[, elast:=simelast]
  elast[, elast_se:=simelast_sd]
  source('preclean.R')
  
  elast_simulated <- copy(elast)
  
  elast <- fread('../externals/elast_results_main.csv') 
  source('preclean.R')
  
# Keep only brands that are common in first/last dataset
  firstobs = with(elast_firstobs, unique(paste(market_id,brand)))
  lastobs = with(elast_lastobs, unique(paste(market_id,brand)))
  bothobs = intersect(firstobs, lastobs)
  
  elast_firstobs = elast_firstobs[paste(market_id,brand)%in%bothobs]
  elast_lastobs = elast_lastobs[paste(market_id,brand)%in%bothobs]
  elast_main_avail = copy(elast)
  elast_main_avail = elast_main_avail[paste(market_id,brand)%in%bothobs]

# set order of variables to appear in figures and tables
ordered_vars = c('rwpspr', 'wpswdst','llen', 'nov12sh')
ordered_vars = ordered_vars[which(ordered_vars%in%elast$variable)]

names(ordered_vars) <- paste0(unlist(sanitize_table(data.frame(ordered_vars))), ' elasticity')

lmerctrl = lmerControl(optimizer ="Nelder_Mead", check.conv.singular="ignore")


winsor_p=.01

notes_sig = 'Significance levels: \\* *p*<.1, \\*\\* *p*<.05, \\*\\*\\* *p*<.01 (two-sided).'
  
for (dframe in grep('^elast', ls(),value=T)) {
  print(dframe)
  for (.var in c('elast', 'elastlt')) {
    eval(parse(text=paste0(dframe,"[!is.na(get(.var)), paste0('w_', .var) := 1/get(paste0(.var, '_se'))]")))
    # rescale
    eval(parse(text=paste0(dframe,"[!is.na(get(.var)), paste0('w_', .var) := get(paste0('w_', .var))/max(get(paste0('w_', .var)))]")))
    eval(parse(text=paste0(dframe,"[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]")))
  }
}  

estimnote = paste0('Elasticities are weighted by inverse standard errors.')
estimnoteshort= 'weighted by inverse standard errors'


notes_base = paste0("^1^ Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Continuous variables have been mean-centred. Standard errors in parentheses.")

notes_loglik = 'Log-likelihood ratio tests computed relative to preceding models.'

# order of covariates in models
covars = c("(Intercept)", 
           "emerging", "gdppercap_rev","gci_rev","hdi_rev",
           "sbbe_std_mc",
           "I(sbbe_std_mc * emerging)",
           "I(sbbe_std_mc * gdppercap_rev)",
           "I(sbbe_std_mc * gci_rev)",
           "I(sbbe_std_mc * hdi_rev)",
           "ln_herf_mc", "ln_market_growth_mc", "appliance", "ln_gini_mc", "local_to_market", "international", "mean_ms_mc")

sigvalue = .1
zval = qnorm(1-sigvalue/2)

```

`r fig('Conceptual framework (see Word document)')`

`r tab('Expected Effects on Marketing Elasticities (see Word document)')`

# Data

```{r table1_countries, echo = FALSE}
tmp=unique(elast, by='country')[, c('country','gci_00.03_gdppercap_s','gci_overall_s','hdi2010', 'developed'),with=F]
setorderv(tmp, c('developed', 'gci_00.03_gdppercap_s'), order=-1L)
first_emerging=match(0,tmp$developed)
tmp[, developed:=NULL]

tmp=sanitize_table(tmp)
colnames(tmp)[2]<-paste0(colnames(tmp)[2], '^2^')
colnames(tmp)[3]<-paste0(colnames(tmp)[3], '^2^')
colnames(tmp)[4]<-paste0(colnames(tmp)[4], '^3^')

kable(tmp, format='html', digits=2, format.args = list(big.mark = ","), initial.zero = FALSE, caption=tab('Development indicators for countries in sample^1^')) %>%
        kable_styling() %>% footnote(number=c('Countries ranked by GDP per capita.', "GDP per capita is in current USD, based on IMF World Economic Outlook Database (April 2010). The Global Competitiveness Index captures microeconomic and macroeconomic foundations of national competitiveness. Both measures are extracted from the World Economic Forum's Global Competitiveness Report (2010/2011, available at https://www.weforum.org/reports/global-competitiveness-report-2010-2011).", "Human Development Index (HDI), capturing a country's living standard, healthcare quality and knowledge base. Measure obtained from the UN Development Programme (2010, http://hdr.undp.org/en/content/human-development-index-hdi). Taiwan's HDI has been imputed as the mean HDI of Thailand and China.")) %>%
  group_rows("Developed economies", 1, first_emerging-1) %>%
  group_rows("Emerging economies", first_emerging, 14)

```

<P style='page-break-before: always'>

```{r table2_category_overview, echo = FALSE}
tmp=data.table(elast)
tmp[, ncountries:=length(unique(country)),by=c('category')]

tmp=tmp[!grepl('allothers|unbranded', brand,ignore.case=T), list(overall_ms=mean(overall_ms), ncountries=mean(ncountries)), by = c('category', 'appliance', 'brand')]

setorderv(tmp, c('category', 'appliance', 'overall_ms'), order=-1L)
tmp[!brand%in%c('unbranded','local'), rank:=1:.N, by = c('category')]
tmp[, brand_include:= rank%in%1:5]

tmp=tmp[, list(cattype=ifelse(unique(appliance)==1, 'Appliances', 'Electronics'), ncountries=unique(ncountries), nbrandsdat=length(unique(brand)), exemplary_brand_names=paste0((unique(brand[brand_include==T])), collapse=', ')), by='category']
tmp=sanitize_table(tmp)
setnames(tmp, 'Top 5 brands', 'Top 5 brands^2^')

try(setorder(tmp, Category),silent=T)

kable(tmp, format='html', caption=tab('Category overview^1^')) %>%
        kable_styling() %>% footnote(number=c('Categories shown in alphabetical order.', 'Top 5 brands are determined on the basis of their average volume share across countries, and are listed in decreasing order of their market share.'))

```

<P style='page-break-before: always'>

`r tab('Variable operationalization')`

**Panel A. Variables in market-share attraction model**

Variable             | Operationalization
-------------------- | ------------------------------------------------------------------
Market share         | Unit sales for brand *i* in period *t*, divided by total unit sales in period *t* in a market (category/country combination).
Price                | Average price of brand *i*, computed as a sales-weighted^1^ average across its SKUs sold in period *t*, expressed in local currency and adjusted by a country's consumer price index^2^.
Distribution         | Average distribution of brand *i*, computed as a sales-weighted^1^ average across its SKUs' store-weighted distribution in period *t* (0 = no market coverage, 100 = full market coverage).
Line length          | Number of unique SKUs sold by brand *i* in period *t*.


**Panel B. Variables in market share attraction model^3^**

Variable                  | Operationalization                                    
-------------------- | ------------------------------------------------------------------
Brand equity       | Sales-based brand equity, derived from the market-share attraction model, standardized by category.
Category concentration  | Herfindahl index in a market (category/country combination).
Category growth       | Average geometric growth rate in a market (category/country combination).^4^
Appliances (vs. electronics)| Dummy variable, equaling 1 for appliances (washing machines, microwaves and refrigerators), 0 for all other categories.
Income inequality    | Gini index in a country.^5^
Domestic (vs. foreign brand) | Dummy variable, equaling 1 if a brand's headquarter is located in the focal country, 0 if not.

^1^ Weights equal to a SKU's unit sales in the most recent quarter (months *t*-2, *t*-1, *t*).

^2^ Consumer price indices obtained from Thomson Reuters Datastream.

^3^ All continuous variables are first logged and then mean-centred before model estimation (except brand strength, which is only mean-centred as this variable can take on negative values). 

^4^ Geometric growth rate is the *n*-th's square root of the ratio of the total number of unit sales in a market in the last year over the brand's total number of unit sales in the first year (both years having 12 months of data), where *n* is equal to the number of years in the observation window.

^5^ Obtained from multiple sources (World Bank, OECD and CIA World Factbook) for the year 2010. When 2010 data was unavailable, we took the closest available estimate.


<P style='page-break-before: always'>
# Results

```{r continue_with_selection, echo=FALSE}
elast_all=data.table(elast)
elast=elast[!is.na(country_of_origin)&!tolower(brand)%in%c('unbranded')]
excluded_brands=setdiff(unique(elast_all$brand), unique(elast$brand))
excluded_brands<-unique(gsub('Allothers.*', 'Composite brands (allothers)', excluded_brands))

elast_laggedx=elast_laggedx[!is.na(country_of_origin)&!tolower(brand)%in%c('unbranded')]
elast_nov=elast_nov[!is.na(country_of_origin)&!tolower(brand)%in%c('unbranded')]
elast_firstobs=elast_firstobs[!is.na(country_of_origin)&!tolower(brand)%in%c('unbranded')]
elast_lastobs=elast_lastobs[!is.na(country_of_origin)&!tolower(brand)%in%c('unbranded')]


```

Reported for a sample of `r length(unique(elast$brand))` unique brands (excluding `r paste0(my_capitalize(excluded_brands), collapse=', ')`).


```{r elasts_full, echo=F,results='asis'}

out = lapply(list(st=c('elast', 'z_elast', 'w_elast'), lt = c('elastlt','z_elastlt','w_elastlt')), function(obj) {
  tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), val_z=get(obj[2]), val_w=get(obj[3]))]
  tmp=tmp[, list(Neffects=.N, 
   						  ftmelast = sum(val*val_w)/sum(val_w),
   						  median_elast = median(val), 
  						  interval90 = paste0('[',paste(sprintf("%.3f",quantile(val, c(.05,.95))),collapse=', '),']')),
  												#  perc_positive = length(which(val_z>=(zval)))/.N, 
  												#  perc_null = length(which(abs(val_z)<zval))/.N, 
  												#  perc_negative = length(which(val_z<=(-zval)))/.N), 
  												by=c('variable')]
  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  return(tmp)
  })
  
iters = list(lt=c('lt', 'Long-term')) #st=c('st', 'Short-term'), 
for (iter in iters) {

  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', format.args = list(big.mark = ","),
        caption=tab(paste0(iter[2], ' elasticities by marketing-mix instrument^1^'),prefix='')) %>% kable_styling() %>% 
        footnote(number=c(paste0('Table reports ', tolower(iter[2]), ' elasticities. The number of observations differs slightly across marketing-mix instruments because some brands in some markets (category/country combinations) do not have variation in these variables.'), estimnote)))
  #cat("<P style='page-break-before: always'>")

  }

```


```{r elast_by_cc, echo=F,results='asis', include=TRUE}

for (byvar in c('country')) {
  tmp=elast[!is.na(elastlt), list(elast = sum(elastlt*w_elastlt)/sum(w_elastlt)), by=c('variable', byvar)]
  setnames(tmp, byvar, 'byvar')
  
  tmp=dcast(tmp,byvar~variable,value.var='elast')
  setnames(tmp, 'byvar', byvar)
  setcolorder(tmp, c(byvar, ordered_vars))
  
  tmp=sanitize_table(tmp)
  setorderv(tmp, colnames(tmp)[1])
  
  cat("<P style='page-break-before: always'>")
  {print(kable(tmp, digits=3, caption = tab(paste0('Long-term elasticities (means by ', byvar, ')^1^'), prefix=''), format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(number=paste0(estimnote, ' Reported by ', ifelse(byvar=='country', 'countries', 'categories'), ' in alphabetical order.')))
  }
}

```	


```{r elasticities_overview, echo = FALSE, results='asis'}
out= NULL

for (i in 1:2) {
  if (i==1) obj=c('elast', 'w_elast', 'z_elast')
  if (i==2) obj=c('elastlt','w_elastlt', 'z_elastlt')
  
  tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                           val_w=get(obj[2]),
                                           val_z=get(obj[3]))]

  # different t-tests

  diff_tests=lapply(c(ttest='ttest', wls='wls',re='re'), function(tvalrep) {
    
    if (tvalrep=='wls') {
    # OLS-based p values   
    diff_tests=rbindlist(lapply(unique(elast$variable), function(.var) {
      data.table(variable=.var, effect=c('constant', 'emerging'), summary(lm(val~1+emerging, weights=val_w,data=tmp[variable==.var]))$coefficients)
    }))
          taddition = paste0('Tests on differences carried out by regressing elasticities (', estimnoteshort, ') on an intercept and an emerging-country indicator. The reported t-value is obtained from the estimate of the emerging-country indicator.')

          }
  
    if (tvalrep=='re') {
    # random effects based p values
      diff_tests=rbindlist(lapply(unique(tmp$variable), function(.var) {
      data.table(variable=.var, effect=c('constant', 'emerging'), summary(lmer(val~1+(1|category) + (1|country) + (1|brand) + emerging, weights=val_w,control = lmerctrl, data=tmp[variable==.var]))$coefficients)[, p:=2*(1-pnorm(abs(get('t value'))))]
    }))
      taddition = paste0('Tests on differences carried out by regressing elasticities (', estimnoteshort, ') on an intercept, an emerging-country indicator and three random effects, for brands, categories, and countries, respectively. The reported t-value is obtained from the estimate of the emerging-country indicator.')

          }
  
   if (tvalrep=='ttest') {
     
  # random effects based p values
    diff_tests=rbindlist(lapply(unique(tmp$variable), function(.var) {
      xemerg=tmp[variable==.var&emerging==1]$val
      xdevel=tmp[variable==.var&emerging==0]$val
      
      tout = t.test(xemerg,xdevel)
      
    data.table(variable=.var, effect=c('emerging'), NA, NA, tout$statistic, tout$p.value)
    }))
    
    taddition = paste0('Tests on differences carried out using a two-sided t-test.')
   }

  setnames(diff_tests, c('variable', 'effect', 'diff_est', 'diff_se', 'diff_t','diff_p'))
  diff_tests=diff_tests[effect=='emerging'][, effect:=NULL]
  diff_tests[,testtype:=tvalrep]
  return(list(diff_tests=diff_tests, notes=taddition))
  })
  
  
  ttests=melt(rbindlist(lapply(diff_tests, function(x) x$diff_tests))[, ':=' (var=variable,variable=NULL)], id.vars=c('var','testtype'))
  
  ttests=dcast(ttests, var~testtype+variable)
  setnames(ttests, 'var', 'variable')
  
  notes<-lapply(diff_tests, function(x) x$notes)
  
  
  tmp = merge(tmp, ttests, by = c('variable'))

  
  tmp=tmp[, list(Neffects= .N, 
                 all_ftmelast = sum(val*val_w)/sum(val_w),
					 		   all_3sig = signstars(sum(val_z,na.rm=T)/sqrt(.N)),
											  
								 dev_Neffects= length(which(!is.na(val[developed==1]))),
			           dev_ftmelast = sum(val[developed==1]*val_w[developed==1])/sum(val_w[developed==1]),
								 dev_3sig = signstars(sum(val_z[developed==1])/sqrt(length(which(!is.na(val[developed==1]))))),
								 
								 em_Neffects= length(which(!is.na(val[developed==0]))),
			           em_ftmelast = sum(val[developed==0]*val_w[developed==0])/sum(val_w[developed==0]),
								 em_3sig = signstars(sum(val_z[developed==0])/sqrt(length(which(!is.na(val[developed==0]))))),
								 wls_t = unique(wls_diff_t), wls_sig = psignstars(unique(wls_diff_p))
								 ), by=c('variable')]

  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  
  out[[i]]<-tmp
  }
  
names(out)<-c('st','lt')

#iters = list(st=c('st', 'Short-term'), lt=c('lt', 'Long-term'))
iters = list(lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', format.args = list(big.mark = ","),
        caption=tab(paste0('Differences in ', tolower(iter[2]), ' elasticities between developed and emerging markets^1^'))) %>% kable_styling() %>% 
        footnote(number=c(paste0(notes_sig, ' The number of observations differs slightly across marketing-mix instruments because some brands in some markets (category/country combinations) do not have variation in these variables.'),estimnote, 'Significance tested using meta-analytic p-value.', notes[2])) %>% add_header_above(c(" " = 1, "All countries" = 3, "Developed markets" = 3, "Emerging markets" = 3, 'Tests on differences' =2)))
}
  
```

<P style='page-break-before: always'>

```{r summarystats, echo=FALSE, results='asis'}

covars_summary <- c('sbbe_std', 'herf', 'market_growth', 'appliance', 'gini', 'local_to_market')

tmp=data.table(elast)
nbrands=length(unique(tmp$brand))
nmarkets=length(unique(tmp$market_id))
tmp = unique(tmp, by = c('market_id','brand', 'emerging'))
nobs=nrow(tmp)

# test for differences in means
diff_tests=rbindlist(lapply(covars_summary, function(.var) {
      tmp[, val:=get(.var)]
      data.table(variable=.var, effect=c('constant', 'emerging'), summary(lm(val~1+emerging,data=tmp))$coefficients)
    }))

setnames(diff_tests, c('variable', 'effect', 'diff_est', 'diff_se', 'diff_t','diff_p'))
diff_tests=diff_tests[effect=='emerging'][, effect:=NULL]


tmp=tmp[, lapply(.SD, function(x) c(mean=mean(x,na.rm=T),sd=sd(x,na.rm=T),min=min(x,na.rm=T), max=max(x,na.rm=T))), by = c('emerging'), .SDcols=c(covars_summary)]
tmp[, var:=rep(c('meancap', 'sdcap','mincap', 'maxcap'),2)]
tmp=melt(tmp, id.var=c('emerging', 'var'))
tmp[, emerging_label:=ifelse(emerging==1, 'emerging', 'developed')]

dtf=dcast(tmp, variable~emerging_label+var)
setcolorder(dtf, c('variable', paste0(rep(c('emerging_', 'developed_'), each=4), rep(c('meancap', 'sdcap', 'mincap','maxcap'),2))))

setnames(dtf, gsub('developed_', '', colnames(dtf)))
setnames(dtf, gsub('emerging_', '', colnames(dtf)))

setkey(diff_tests, variable)
setkey(dtf, variable)

dtf[diff_tests, ':=' (comb_t=i.diff_t, comb_sig=gsub('[*]', '\\*', psignstars(i.diff_p)))]

dtf=sanitize_table(dtf)


print(kable(dtf, format='html', initial.zero = FALSE, digits=3,caption = tab(paste0('Summary statistics for covariates in second-stage analysis, split by a country\'s development status^1^'))
      ) %>% kable_styling() %>% footnote(number=c(paste0('Summary statistics for variables (prior to the log-operation and mean-centering) are computed across the ', prettyNum(nobs, big.mark=','), ' observations in our sample.'),'Tests on differences carried out by regressing variables on an intercept and an emerging-country indicator. The reported t-value is obtained from the estimate of the emerging-country indicator.')) %>% add_header_above(c(" " = 1, "Emerging markets" = 4, "Developed markets" = 4, "Test on differences^2^"=2)))

```


```{r analysis_for_all_mmix, results = 'asis', include = T, echo=FALSE}

upd_models = list(m4 = .~1 + emerging + sbbe_std_mc + I(sbbe_std_mc*emerging)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market)
                   
out1=regmodel(formula=c(upd_models), dat=elast, model='lmer')

cat("<P style='page-break-before: always'>")

printout(out1, 'lt', title = tab(paste0('Regression with long-term elasticities'), prefix=''), vars=ordered_vars,  notes=notes_base, covariate_choices = covars)

```

```{r plot_be_interaction, fig.width=16,fig.height=6,echo=F}


elast[, ':=' (l_emerging=ifelse(emerging==1,'Emerging market','Developed market'),
             l_brandequity=ifelse(sbbe_std_mc>median(sbbe_std_mc,na.rm=T), 'strong brand','weak brand')),by=c('variable','category','country','market_id')]


sims = elast[, list(est=sum(elastlt*w_elast)/sum(w_elast)), by = c('variable', 'l_brandequity', 'l_emerging')]
sims[, lbl:=formatC(round(est,2), format='f',digits=2)]
lbl=c('2a)', '2b)', '2c)')
cnt=1
out <- lapply(ordered_vars, function(mod) {
  simtmp=sims[variable==mod]
  p<-ggplot(simtmp, aes(x=l_brandequity,y=est, fill = l_emerging)) + theme_tufte() +geom_bar(stat="identity", position = 'dodge', width= .5) + geom_text(aes(label=lbl),vjust=ifelse(mod=='rwpspr', 1.2,-.95), hjust=.5,size=2.2,position = position_dodge(0.5)) + ggtitle(paste0(lbl[cnt], ' ', gsub('Line length', 'Line-length', rename.fkt(mod)), ' elasticity')) + xlab('Brand equity') + ylab('Mean elasticity') + labs(fill="Country\'s degree of development  ") + scale_fill_grey(start = 0, end = .9)
  cnt<<-cnt+1
    return(p)

})

p <- ggarrange(plotlist=out, nrow=ifelse(length(ordered_vars)==3,1,2), ncol=ifelse(length(ordered_vars)==3,3,2), common.legend=TRUE, legend='bottom')
full_plot = annotate_figure(p, top=fig('Elasticity plots'), bottom = text_grob('Note: Plots show estimated long-term marketing-mix elasticities (weighted by inverse standard errors), based on a country\'s degree of development (DM versus EM), and a median split on brand equity.', size= 8, just='left', x = 0))
full_plot

png('../output/elasticity_plots.png', res=200, units='in', height=4, width=9)
print(p)
dev.off()



```

```{r reset, echo=FALSE,results='asis'}
tableno<<-0
figureno<<-0
cat("<P style='page-break-before: always'>")
  
```
# Appendix

```{r sample_origin, echo=FALSE, results='asis'}

cols =  c('country_of_origin')
tmp = elast[, list(.N), by = c('brand',cols)]
tmp = tmp[, list(nbrands=length(unique(brand)), all_brands=paste(brand[order(brand)], collapse=', ')), by = cols]
tmp[country_of_origin==''|is.na(country_of_origin), country_of_origin := 'Country not available']
tmp[, country_of_origin:=my_capitalize(country_of_origin)]

setorderv(tmp, 'nbrands', order=-1L)
setcolorder(tmp, c('country_of_origin', 'nbrands', 'all_brands'))

tmp=sanitize_table(tmp)

kable(tmp, caption = tab('Country-of-origins for brands in sample^1^', prefix ='A'),format='html') %>%
        kable_styling() %>% footnote(number=paste0('Countries are ordered by the number of brands from a given country; brand names are listed alphabetically.'))

```

<P style='page-break-before: always'>
```{r VIFS, echo=FALSE,results='asis', include=FALSE}

m1 = ~1+ appliance + ln_market_growth_mc + ln_herf_mc + local_to_market  + ln_overall_prindexavg_mc + sbbe_std_mc

m<-lm(update(elast~., m1), data=elast[variable=='llen'])

frame1=data.frame(vif(m))
colnames(frame1) <- c('VIF')
frame1$variable=rownames(frame1)
rownames(frame1)<-NULL
frame1=frame1[, c('variable','VIF')]
frame1=sanitize_table(frame1)
cat("<P style='page-break-before: always'>")

if(0){
kable(frame1,format='html', caption = tab('Assessing multicollinearity^1^', prefix='A'))%>% kable_styling() %>% footnote(number=paste0('Table reports VIFs values calculated in regression models using main effects for all variables listed above (i.e., excluding brand, category, and country effects).'))
}
```


```{r overview2, echo=FALSE, results='asis'}
tmp = elast_all[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))

tabl=sanitize_table(tabl)
setorder(tabl, Category)
kable(tabl, caption = tab('Overview of markets (category/country combination) in the sample (with number of selected brands used in model estimation indicated per cell^1^)', prefix='A'))%>% kable_styling() %>% footnote(number=paste0('Number of brands include the composite brand, which aggregates all brands with market shares lower than 1% in 5 consecutive years (4 years for tablets).'))

```

<P style='page-break-before: always'>

```{r attributes, echo = FALSE, results= 'asis'}

# for each category

attributes <- suppressWarnings(melt(brand_panel[!is.na(usalessh), c('category', grep('^attr', colnames(brand_panel),value=T)),with=F], id.vars=c('category')))

attributes[, na:=all(is.na(value)),by=c('category','variable')]

attr = attributes[na==F, list(nobs = .N, meancap=mean(value), sdcap=sd(value), mincap=min(value), maxcap=max(value)),by=c('category','variable')]
setorder(attr,category,variable)
.vars=c('nobs','meancap','sdcap', 'mincap', 'maxcap')
for (.var in .vars) attr[, (.var):=as.character(formatC(get(.var), big.mark=',',digits=ifelse(.var=='nobs', 0, 3), format = 'f'))]

attr<-attr[!grepl('freezernotestimable', variable)]
setnames(attr, 'variable','Attribute')
tabl=sanitize_table(attr)
setorder(tabl, Category)

print(kable(tabl, digits=3, caption = tab('Overview of physical search attributes per category^1^', prefix='A')) %>% kable_styling() %>% footnote(number=c(paste0('The unit of analysis is the brand-month level. Indicator variables are either 0 or 1 at the SKU-month-level; when aggregating them to the brand-month level for the analysis, they are averaged and hence measure the share of a brand\'s SKUs that carry a particular product attribute.'))))
```

<P style='page-break-before: always'>

```{r summarystats_msmodel, echo=FALSE, results='asis'}

covars_summary <- c('usalessh', gsub('rwpspr', 'rwpsprd', ordered_vars))

tmp=data.table(brand_panel)
nbrands=length(unique(brand_panel$brand))
nmarkets=length(unique(brand_panel$market_id))
nobs=nrow(tmp)

tmp=tmp[, lapply(.SD, function(x) c(median=median(x,na.rm=T),firstqnt=quantile(x,.25,na.rm=T),thirdqnt=quantile(x,.75,na.rm=T))), .SDcols=c(covars_summary)]


tmp[, var:=rep(c('median', 'firstqnt','thirdqnt'),1)]
tmp=melt(tmp, id.var=c('var'))

dtf=dcast(tmp, variable~var)
setcolorder(dtf, c('variable', rep(c('median', 'firstqnt','thirdqnt'),1)))

### add correlation
give_cor <- function(cordat=data.frame(brand_panel[, covars_summary,with=F])) {
  correl=cor(cordat,use='pairwise.complete')
  N=matrix(double(prod(dim(correl))),ncol=ncol(cordat))
  t=N
  p=N
  for (i in 1:nrow(correl)) {
    for (j in 1:ncol(correl)) {
      N[i,j]=length(which(complete.cases(cordat[,c(i,j)])))
      t[i,j]=sqrt(N[i,j]-2)*(correl[i,j]/sqrt(1-correl[i,j]^2))
      p[i,j]=dt(t[i,j], df=N[i,j]-2)
    }
  }
return(list(cor=correl,p=p))
}

correl = give_cor(data.frame(brand_panel[, covars_summary,with=F]))

sink('../output/tableA4.txt')
correl$cor
correl$p
sink()

dtf=cbind(dtf,correl$cor[,-ncol(correl$cor)])


dtf=sanitize_table(dtf)


print(kable(dtf, format='html', initial.zero = FALSE, digits=3,caption = tab(paste0('Summary statistics and correlations for variables in market share attraction model^1^'),prefix='A')) %>% kable_styling() %>% footnote(number=c(paste0('Summary statistics and correlations for variables (prior to the log-operation and mean-centering) are computed across ', prettyNum(nobs, big.mark = ','), ' observations in our sample.'),'Converted to USD.')) %>% add_header_above(c(" " = 1, "Summary statistics" = 3, "Correlations" = length(covars_summary)-1)))

```


```{r correl, echo=FALSE, results = 'asis'}

tmp = dcast(elast,market_id+brand~variable, value.var=c('elast', 'elastlt'))

#for (var in grep('elast', colnames(tmp),value=T)) {
#  tmp[, (paste0('mc_', var)):=get(var)-mean(get(var),na.rm=T), by = c('market_id')]
#  }

printtmp=tmp[, grep('elastlt[_]', colnames(tmp),value=T) ,with=F]
setnames(printtmp, gsub('elastlt[_]','',colnames(printtmp)))

setcolorder(printtmp, ordered_vars)

setnames(printtmp, 'llen', 'llendash')

setnames(printtmp, paste0(rename.fkt(colnames(printtmp)), ' elasticity'))


tmp2=corstars(printtmp, method=c("pearson"),removeTriangle=c('upper'),result='none')
#, caption = tab('Correlation among long-term marketing-mix elasticities', prefix='A'))
kable(tmp2, format='html', caption=tab('Correlation among long-term marketing-mix elasticities',prefix='A')) %>%
        kable_styling() 



```


```{r elast_by_cc2, echo=F,results='asis', include=TRUE}

for (byvar in c('category')) {
  tmp=elast[!is.na(elastlt), list(elast = sum(elastlt*w_elastlt)/sum(w_elastlt)), by=c('variable', byvar)]
  setnames(tmp, byvar, 'byvar')
  
  tmp=dcast(tmp,byvar~variable,value.var='elast')
  setnames(tmp, 'byvar', byvar)
  setcolorder(tmp, c(byvar, ordered_vars))
  
  tmp=sanitize_table(tmp)
  setorderv(tmp, colnames(tmp)[1])
  
  cat("<P style='page-break-before: always'>")
  {print(kable(tmp, digits=3, caption = tab(paste0('Long-term elasticities (means by ', byvar, ')^1^'), prefix='A'), format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(number=paste0(estimnote, ' Reported by ', ifelse(byvar=='country', 'countries', 'categories'), ' in alphabetical order.')))
  }
}


```	


```{r newanalysis_robust, results = 'asis', include = TRUE, echo=FALSE}
# formulas for models

elast_backup = data.table(elast)

elast_backup[!is.na(elastlt), mean_ms_mc := mean_ms-mean(mean_ms,na.rm=T), by = c('variable')]

elast_backup[, international:=ifelse(ncountries>=2,1,0)]

elast_backup[, gdppercap_rev := -ln_gci_00.03_gdppercap_s_mc]
elast_backup[, gci_rev := -ln_gci_overall_s_mc]
elast_backup[, hdi_rev := -ln_hdi2010_mc]

upd_models = list(
  main = .~1 + emerging + sbbe_std_mc + I(sbbe_std_mc*emerging)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market,
  
marketshare = .~1 + emerging + sbbe_std_mc + I(sbbe_std_mc*emerging)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market + mean_ms_mc,

international = .~1 + emerging + sbbe_std_mc + I(sbbe_std_mc*emerging)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market + international,

gdp = .~1 + gdppercap_rev + sbbe_std_mc + I(sbbe_std_mc*gdppercap_rev)+ (1|brand) + (1|category) + (1|country) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market,

gci = .~1 + gci_rev + sbbe_std_mc + I(sbbe_std_mc*gci_rev)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market,

hdi = .~1 + hdi_rev + sbbe_std_mc + I(sbbe_std_mc*hdi_rev)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market
)

out=regmodel(formula=c(upd_models), dat=elast_backup, model='lmer')

outlagx = regmodel(formula=list(lagx=upd_models$main), dat=elast_laggedx, model='lmer')

elast_backup[is.na(gamma_lagms), gamma_lagms:=0]
elast_backup[, elastlt := beta/(1-gamma_lagms)]

out2=regmodel(formula=list(lambda=upd_models$main), dat=elast_backup, model='lmer')

outsim=regmodel(formula=list(simulated=upd_models$main), dat=elast_simulated, model='lmer')


outx = NULL

  for (mod in names(out)) {
    outx[[mod]]$variable=out[[mod]]$variable
    outx[[mod]]$st=c(out[[mod]]$st$main, out[[mod]]$st$gdp, out[[mod]]$st$gci, out[[mod]]$st$hdi, out[[mod]]$st$marketshare, out[[mod]]$st$international, out2[[mod]]$st$lambda, outlagx[[mod]]$st$lagx, outsim[[mod]]$st$simulated)
    outx[[mod]]$lt=c(out[[mod]]$lt$main, out[[mod]]$lt$gdp, out[[mod]]$lt$gci, out[[mod]]$lt$hdi, out[[mod]]$lt$marketshare, out[[mod]]$lt$international, out2[[mod]]$lt$lambda, outlagx[[mod]]$lt$lagx, outsim[[mod]]$lt$simulated)
  }

#sink('test.htm')
for (i in seq(along=ordered_vars)) {
  cat("<P style='page-break-before: always'>")

  printout(outx, 'lt', title = tab(paste0('Robustness checks for long-term ', tolower(gsub('ity', 'ities', gsub('Line length', 'Line-length', names(ordered_vars[i])))), ''), prefix='A'), vars=ordered_vars[i],  notes=paste0(gsub('term elasticities', 'term elasticities (all models; except beta/(1-gamma) in model 4)', notes_base), ' Model (1) is the focal model; models (2)-(4) replace the emerging market indicator by alternative (continuous) metrics that measure a country\'s degree of development; because these metrics are increasing with a country\'s degree of development, they have been reverse-coded in model estimation, so that coefficients between model (1) and models (2)-(4) can directly be compared. Model (5) controls for a brand\'s market share, while model (6) controls for international brands (indicator variable, 1 for brands active in more than 1 country, 0 otherwise). Model (7) replaces long-term elasticities by beta/(1-gamma). Elasticities in model (8) are calculated from an alternative market share attraction model, allowing for marketing-mix and brand-specific dynamics by adding lagged marketing mix variable (but removing the common carry-over parameter); elasticities in model (9) are dynamically simulated, see Web Appendix B for the details.'), covariate_choices = covars, table.layout.overwrite=c('-c#m-t-a-n'),
           colnames_overwrite=c('Main model', 'Log GDP', 'Log GCI','Log HDI', 'Controlling for marketshare', 'Controlling for international brands','DV is beta/(1-gamma)', 'Marketing-mix and brand-specific dynamics', 'Dynamic simulation'), colsep_overwrite = rep(1,9))
}

#sink()

```

```{r elasticities_advertising, echo = FALSE, results='asis'}
  
out= NULL
for (i in 1:2) {
    if (i==1) obj=c('elast', 'w_elast', 'z_elast')
    if (i==2) obj=c('elastlt','w_elastlt', 'z_elastlt')
    
    adv = copy(elast_adv[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))])
    
    # retain markets with adv
    tmp = adv[, list(has_adv=any(variable%in%'adv')),by=c('market_id', 'brand')]
    setkey(tmp, market_id, brand)
    setkey(adv, market_id, brand)
    adv[tmp, has_adv:=i.has_adv]
    adv=adv[has_adv==T]
    
    setkey(adv, market_id, brand)
    
    tmp_matched = copy(elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))])
    setkey(tmp_matched, market_id, brand)
    
    adv[, market_brand:=paste(market_id,brand)]
    tmp_matched[, market_brand:=paste(market_id,brand)]
    
    tmp_matched=tmp_matched[market_brand%in%adv$market_brand]
    
    cols = intersect(colnames(adv),colnames(tmp_matched))
    
    tmp_combined = rbind(cbind(adv[, cols,with=F], type='adv'), cbind(tmp_matched[, cols, with=F],type='noadv'))
    
   
    # different t-tests
  
    diff_tests=lapply(c(wls='wls'), function(tvalrep) {
      
      if (tvalrep=='wls') {
      # OLS-based p values   
      diff_tests=rbindlist(lapply(unique(tmp_combined$variable), function(.var) {
        data.table(variable=.var, effect=c('constant', 'adv'), summary(lm(val~1+I(type=='adv'), weights=val_w,data=tmp_combined[variable==.var]))$coefficients)
      }))
            taddition = paste0('Tests on differences carried out by regressing elasticities (', estimnoteshort, ') on an intercept and an indicator variable which is 1 if advertising was included in the model, and 0 otherwise. Reported t-value is obtained from the estimate of the indicator variable.')
  
            }
    
    diff_tests<-diff_tests[!variable=='adv']

    setnames(diff_tests, c('variable', 'effect', 'diff_est', 'diff_se', 'diff_t','diff_p'))
    diff_tests=diff_tests[effect=='adv'][, effect:=NULL]
    diff_tests[,testtype:=tvalrep]
    return(list(diff_tests=diff_tests, notes=taddition))
    })
    
    
    ttests=melt(rbindlist(lapply(diff_tests, function(x) x$diff_tests))[, ':=' (var=variable,variable=NULL)], id.vars=c('var','testtype'))
    
    ttests=dcast(ttests, var~testtype+variable)
    setnames(ttests, 'var', 'variable')
    
    notes<-lapply(diff_tests, function(x) x$notes)
    
    
    tmp_combined = merge(tmp_combined, ttests, all.x=T,all.y=F,by = c('variable'))
    
    tmp_combined[is.na(wls_diff_p),wls_diff_p:=Inf]
    
    tmp=tmp_combined[, list(adv_Neffects= length(which(!is.na(val[type=='adv']))),
				           adv_ftmelast = sum(val[type=='adv']*val_w[type=='adv'])/sum(val_w[type=='adv']),
									 adv_3sig = signstars(sum(val_z[type=='adv'])/sqrt(length(which(!is.na(val[type=='adv']))))),
									 nadv_Neffects= length(which(!is.na(val[!type=='adv']))),
				           nadv_ftmelast = sum(val[!type=='adv']*val_w[!type=='adv'])/sum(val_w[!type=='adv']),
									 nadv_3sig = signstars(sum(val_z[type=='adv'])/sqrt(length(which(!is.na(val[!type=='adv']))))),
									 wls_t = unique(wls_diff_t), 
									 wls_sig = psignstars(unique(wls_diff_p))), by=c('variable')]
    
    
  tmp=tmp[match(c('adv', ordered_vars), variable)]
  setnames(tmp, 'variable', 'mmixinstr')

  out[[i]]<-tmp
  }

  
names(out)<-c('st','lt')

stats_markets = length(unique(adv$market_id))
stats_brands = length(unique(adv$market_brand))
stats_categories = length(unique(adv$category))

stats_marketnames = sapply(c('china','hong kong'), function(x) {
  x = unlist(sanitize_table(data.frame(unique(adv[country==x]$category))))
  x=x[order(x)]
  
  return(paste0(x, collapse= ', '))
})

stats_categorynames = unlist(sanitize_table(data.frame(unique(adv$category))))
stats_categorynames=paste0(stats_categorynames[order(stats_categorynames)], collapse = ', ')

mainnote = paste0('We add to our main model the advertising expenditures for ', stats_brands, ' brands, and re-estimate marketing-mix elasticities in all markets for which advertising data is available to us (in total ', stats_markets, ' markets from ', stats_categories, ' categories in two countries, China and Hong Kong). We then compare the marketing-mix elasticities from this model to those elasticities estimated from our main model; in the comparison, we only include those ', stats_brands, ' brands for which advertising expenditures are available.')

iters = list(lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', format.args = list(big.mark = ","),
        caption=tab(paste0('Differences in ', tolower(iter[2]), ' elasticities in models with and without advertising spending^1^'),prefix='A')) %>% kable_styling() %>% 
        footnote(number=c(paste0(notes_sig, ' ', mainnote),estimnote, 'Significance tested using meta-analytic p-value.', notes[1])) %>% add_header_above(c(" " = 1, "Advertising included" = 3, "Main model (advertising not included)" = 3, 'Tests on differences' =2)))
}
```

```{r elasticities_novelty, echo = FALSE, results='asis'}
  
out= NULL
for (i in 2) {
    if (i==1) obj=c('elast', 'w_elast', 'z_elast')
    if (i==2) obj=c('elastlt','w_elastlt', 'z_elastlt')
    
    nov = copy(elast_nov[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))])
    
    setkey(nov, market_id, brand)
    tmp_matched = copy(elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))])
    setkey(tmp_matched, market_id, brand)
    
    nov[, market_brand:=paste(market_id,brand)]
    tmp_matched[, market_brand:=paste(market_id,brand)]
    
    tmp_matched=tmp_matched[market_brand%in%nov$market_brand]
    
    cols = intersect(colnames(nov),colnames(tmp_matched))
    
    tmp_combined = rbind(cbind(nov[, cols,with=F], type='nov'), cbind(tmp_matched[, cols, with=F],type='nonov'))
    
   
    # different t-tests
  
    diff_tests=rbindlist(lapply(unique(tmp_combined$variable), function(.var) {
        data.table(variable=.var, effect=c('constant', 'nov'), summary(lm(val~1+I(type=='nov'), weights=val_w,data=tmp_combined[variable==.var]))$coefficients)
      }))
    
    taddition = paste0('Tests on differences carried out by regressing elasticities (', estimnoteshort, ') on an intercept and an indicator variable which is 1 if new-product activity was included in the model, and 0 otherwise. Reported t-value is obtained from the estimate of the indicator variable.')
  
  
    
    diff_tests<-diff_tests[!grepl('^nov', variable)]
    
    setnames(diff_tests, c('variable', 'effect', 'diff_est', 'diff_se', 'diff_t','diff_p'))
    diff_tests=diff_tests[effect=='nov'][, effect:=NULL]
    setcolorder(diff_tests, 'variable')
    
    
    tmp_combined = merge(tmp_combined, diff_tests, all.x=T,all.y=F,by = c('variable'))
    
    tmp_combined[is.na(diff_p),diff_p:=Inf]
    
    tmp=tmp_combined[, list(nov_Neffects= length(which(!is.na(val[type=='nov']))),
				           nov_ftmelast = sum(val[type=='nov']*val_w[type=='nov'])/sum(val_w[type=='nov']),
									 nov_3sig = signstars(sum(val_z[type=='nov'])/sqrt(length(which(!is.na(val[type=='nov']))))),
									 nnov_Neffects= length(which(!is.na(val[!type=='nov']))),
				           nnov_ftmelast = sum(val[!type=='nov']*val_w[!type=='nov'])/sum(val_w[!type=='nov']),
									 nnov_3sig = signstars(sum(val_z[type=='nov'])/sqrt(length(which(!is.na(val[!type=='nov']))))),
									 wls_t = unique(diff_t), 
									 wls_sig = psignstars(unique(diff_p))), by=c('variable')]
    
    
  tmp=tmp[match(c('nov12sh', ordered_vars), variable)]
  setnames(tmp, 'variable', 'mmixinstr')

  out[[i]]<-tmp
  }

  
names(out)<-c('st','lt')

stats_markets = length(unique(nov$market_id))
stats_brands = length(unique(nov$market_brand))
stats_categories = length(unique(nov$category))


mainnote = paste0('We add to our main model a variable that captures a brand\'s new-product activity (defined as the number of SKUs introduced by the focal brand in a rolling window of one year (t-11, t-10, ..., t), expressed as share of the total number of unique SKUs sold by the focal brand over the same period; 0 = none of the SKUs is new, 100 = all of the SKUs are new). The model is then re-estimated to obtain long-term marketing mix elasticities in all ', stats_markets, ' markets. We then compare the marketing-mix elasticities from this model to those elasticities estimated from our main model.')

iters = list(lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', format.args = list(big.mark = ","),
        caption=tab(paste0('Differences in ', tolower(iter[2]), ' elasticities in models with and without new-product activity^1^'),prefix='A')) %>% kable_styling() %>% 
        footnote(number=c(paste0(notes_sig, ' ', mainnote),estimnote, 'Significance tested using meta-analytic p-value.', taddition)) %>% add_header_above(c(" " = 1, "New-product activity included" = 3, "Main model (new-product activity not included)" = 3, 'Tests on differences' =2)))
}
```

```{r analysis_for_all_mmix_wnovelty, results = 'asis', include = T, echo=FALSE}

# common to all

upd_models = list(m4 = .~1 + emerging + sbbe_std_mc + I(sbbe_std_mc*emerging)+ (1|country) + (1|category) + (1|brand) + ln_herf_mc + ln_market_growth_mc + appliance + ln_gini_mc + local_to_market)
                   
out1=regmodel(formula=c(upd_models), dat=elast_main_avail, model='lmer')
out2=regmodel(formula=c(upd_models), dat=elast_firstobs, model='lmer')
out3=regmodel(formula=c(upd_models), dat=elast_lastobs, model='lmer')

#sink('test.html')
cat("<P style='page-break-before: always'>")



outx = NULL

  for (mod in names(out1)) {
    outx[[mod]]$variable=out1[[mod]]$variable
    outx[[mod]]$st=c(out1[[mod]]$st$m4, out2[[mod]]$st$m4, out3[[mod]]$st$m4)
    outx[[mod]]$lt=c(out1[[mod]]$lt$m4, out2[[mod]]$lt$m4, out3[[mod]]$lt$m4)
  }


#  printout(outx, 'lt', title = tab(paste0('Robustness checks for long-term ', tolower(gsub('ity', 'ities', gsub('Line length', 'Line-length', names(ordered_vars[i])))), ''), prefix='A'), vars=ordered_vars[i],  notes=paste0(gsub('term elasticities', 'term elasticities (all models; except beta/(1-gamma) in model 4)', notes_base), ' Model (1) is the focal model; models (2)-(4) replace the emerging market indicator by alternative (continuous) metrics that measure a country\'s degree of development; because these metrics are increasing with a country\'s degree of development, they have been reverse-coded in model estimation, so that coefficients between model (1) and models (2)-(4) can directly be compared. Model (5) controls for a brand\'s market share, while model (6) controls for international brands (indicator variable, 1 for brands active in more than 1 country, 0 otherwise). Model (7) replaces long-term elasticities by beta/(1-gamma). Elasticities in model (8) are calculated from an alternative market share attraction model, allowing for marketing-mix and brand-specific dynamics by adding lagged marketing mix variable (but removing the common carry-over parameter); elasticities in model (9) are dynamically simulated, see Web Appendix B for the details.'), covariate_choices = covars, table.layout.overwrite=c('-c#m-t-a-n'),
 #          colnames_overwrite=c('Main model', 'Log GDP', 'Log GCI','Log HDI', 'Controlling for marketshare', 'Controlling for international brands','DV is beta/(1-gamma)', 'Marketing-mix and brand-specific dynamics', 'Dynamic simulation'), colsep_overwrite = rep(1,9))
#}


printout(outx, 'lt', title = tab(paste0('Robustness check: Selected sample for which both early and late brands are available'), prefix='A'), vars=c(ordered_vars),  notes=notes_base, covariate_choices = covars, dep.var.labels.include=T)

#printout(out2, 'lt', title = tab(paste0('Robustness check: Early sample'), prefix='A'), vars=c(ordered_vars),  notes=notes_base, covariate_choices = covars)
#printout(out3, 'lt', title = tab(paste0('Robustness check: Late sample'), prefix='A'), vars=c(ordered_vars),  notes=notes_base, covariate_choices = covars)
#sink()

```

# try out WLS

elast_firstobs[, time := 'first']
elast_lastobs[, time := 'last']
elast_time = rbind(elast_firstobs, elast_lastobs,fill=T)
elast_time[, emerging_last:=as.numeric(as.numeric(time=='last')*as.numeric(emerging))]
elast_time[, developed_last:=as.numeric(as.numeric(time=='last')*as.numeric(1-emerging))]

for (.var in ordered_vars) {
  print(summary(lm(elastlt~1+emerging+emerging_last+developed_last, data=elast_time[variable==.var], weight=1/elastlt_se)))
}




