---
title: "GfK Singapore - Results"
output:
  html_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(plyr)
#library(psych)

libs_to_load <- c('data.table', 'stargazer', 'knitr', 'xtable', 'lme4', 'car', 'kableExtra', 'stringi', 'ggplot2')
for (lib in libs_to_load) eval(parse(text=paste('library(', lib, ')')))

options(xtable.comment = FALSE)
options(knitr.kable.NA = '')

# Load data
  #elast <- fread('../externals/elast_results_MCI_wlag_wotrend.csv')
  elast <- fread('../externals/elast_results_MCI_wolag_trend.csv')

# Load auxilary functions
  source('proc_auxilary.R')
  source('proc_rename.R')

# Preclean data
  source('preclean.R')
  
# set order of variables to appear in figures and tables
ordered_vars = c('rwpspr', 'wpswdst','llen','nov6sh')

# fix 'standard' covariates
form_main_model = .~1+ (1|brand) + (1|category) + (1|country) + emerging + appliance + ln_market_growth_mc + ln_herf_mc + local_to_market + ln_overall_prindex_mc + sbbe_std_mc 

form_interact = ~1+ (1|brand) + (1|category) + (1|country) + emerging + appliance + I(appliance*emerging) + ln_market_growth_mc + I(ln_market_growth_mc*emerging) + ln_herf_mc + I(ln_herf_mc*emerging) + local_to_market + I(local_to_market*emerging) + ln_overall_prindex_mc + I(ln_overall_prindex_mc*emerging) + sbbe_std_mc + I(sbbe_std_mc*emerging)


form_random_component = .~1+ (1|brand) + (1|category) + (1|country)

form_random_component_FE = .~1+ (1|brand) + (1|category) + as.factor(country)

form_std = .~. + appliance + ln_market_growth_mc + ln_herf_mc + local_to_market + ln_overall_prindex_mc


form_interact_gci = ~1+ (1|brand) + (1|category) + (1|country) + gcifactor_mc + appliance + I(appliance*gcifactor_mc) + ln_market_growth_mc + I(ln_market_growth_mc*gcifactor_mc) + ln_herf_mc + I(ln_herf_mc*gcifactor_mc) + local_to_market + I(local_to_market*gcifactor_mc) + ln_overall_prindex_mc + I(ln_overall_prindex_mc*gcifactor_mc) + sbbe_std_mc + I(sbbe_std_mc*gcifactor_mc)


# choice for main 'brand strength' variable
form_modelbasis = update.formula(form_random_component, form_std)
form_extraregressor = .~. + sbbe_std_mc

winsor_p=.05

#estimtype = 'winsor-onesided'
estimtype = 'weighted'
#estimtype = 'winsor-twosided'

# apply winsorization
# 1-sided
if (estimtype=='winsor-onesided') {
  
  for (.var in c('elast', 'elastlt')) {
    elast[!is.na(get(.var)), (.var) := winsor_onesided(get(.var), fraction=winsor_p, ifelse(variable=='rwpspr', 'right','left')), by=c('variable')]
    elast[!is.na(get(.var)), paste0('w_', .var) := 1]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities have been winsorized at ', winsor_p*100, '%, left-sided for all variables except price.')
  
}

# 2-sided
if (estimtype=='winsor-twosided') {
  
  for (.var in c('elast', 'elastlt')) {
    elast[!is.na(get(.var)), (.var) := winsor_onesided(get(.var), fraction=winsor_p, side='both'), by=c('variable')]
    elast[!is.na(get(.var)), paste0('w_', .var) := 1]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities have been winsorized at ', winsor_p*100, '%, two-sided.')
  
}

if (estimtype=='weighted') {
  
  for (.var in c('elast', 'elastlt')) {

    elast[!is.na(get(.var)), paste0('w_', .var) := 1/get(paste0(.var, '_se'))]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities are weighted by inverse standard errors.')
  
}
```

# Data

```{r table1_countries, echo = FALSE}
tmp=unique(elast, by='country')[, c('country','gci_00.03_gdppercap_s','gci_overall_s','hdi2010', 'developed'),with=F]
setorderv(tmp, c('developed', 'gci_00.03_gdppercap_s'), order=-1L)
first_emerging=match(0,tmp$developed)
tmp[, developed:=NULL]

kable(sanitize_table(tmp), format='html', initial.zero = FALSE, caption=tab('Development indicators for countries in sample')) %>%
        kable_styling() %>% footnote(general='Countries ranked by GDP per capita.', alphabet=c("GDP per capita in current USD, 2010 data, IMF World Economic Outlook Database (April 2010). Extracted from the World Economic Forum's Global Competitiveness Report (2010/2011, available at https://www.weforum.org/reports/global-competitiveness-report-2010-2011).", "Global Competitiveness Index captures microeconomic and macroeconomic foundations of national competitiveness, and is exctracted from the World Economic Forum's Global Competitiveness Report (link see above).", "Human Development Index (HDI), 2010 data, obtained from UN Development Programme (http://hdr.undp.org/en/content/human-development-index-hdi). Taiwan's HDI has been imputed as the mean HDI of Thailand and China.")) %>%
  group_rows("Developed economies", 1, first_emerging-1) %>%
  group_rows("Emerging economies", first_emerging, 14)

```

```{r table2_category_overview, echo = FALSE}
tmp=data.table(elast)
tmp[, ncountries:=length(unique(country)),by=c('category')]

tmp=tmp[, list(overall_ms=mean(overall_ms), ncountries=mean(ncountries)), by = c('category', 'appliance', 'brand')]

setorderv(tmp, c('category', 'appliance', 'overall_ms'), order=-1L)
tmp[!brand%in%c('unbranded','local'), rank:=1:.N, by = c('category')]
tmp[, brand_include:= rank%in%1:5]


tmp=tmp[, list(cattype=ifelse(unique(appliance)==1, 'Appliance', 'Electronics'), ncountries=unique(ncountries), nbrands=length(unique(brand)), exemplary_brand_names=paste0((my_capitalize(unique(brand[brand_include==T]))), collapse=', ')), by='category']
tmp=sanitize_table(tmp)

try(setorder(tmp, Category),silent=T)

kable(tmp, format='html', caption=tab('Category overview')) %>%
        kable_styling() %>% footnote(general='Categories shown in alphabetical order. Top 5 brands are determined on the basis of their average volume share across countries, and are listed in decreasing order of their market shares.')

```

# Market share model

`r tab('Variable operationalization for market share attraction model')`


Variable             | Operationalization
-------------------- | ------------------------------------------------------------------
Market share         | Unit sales for brand *i* in period *t*, devided by total unit sales in period *t* in a market.
Price                | Sales-weighted^1^ average of each SKU's price sold by brand *i* in period *t*, expressed in local currency and adjusted by a country's consumer price index^2^.
Distribution         | Sales-weighted^1^ distribution of each of brand *i*'s SKUs' store-weighted distribution in period *t* (0 = no market coverage, 100 = full market coverage).
Line length          | Number of unique SKUs sold by brand *i* in period *t*.
New product activity | Number of SKUs introduced by brand *i* in a rolling window of 6 months (*t-5*, *t-4*, *...*, *t*), expressed as a share of the total number of unique SKUs sold by brand *i* over the same period.

Notes:

^1^ Weights equal to a SKU's unit sales in the most recent quarter (t-2, t-1, t).

^2^ Consumer price index obtained from Thomson Reuters Datastream.

```{r elasticities_overview, echo = FALSE, results='asis'}
  sigvalue = .1 # .1-level of significance
  
  zval = qnorm(1-sigvalue/2)

  out = lapply(list(st=c('elast', 'w_elast', 'z_elast'), lt = c('elastlt','w_elastlt', 'z_elastlt')), function(obj) {
               
    tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))]
    
    tmp=tmp[, list(Neffects= .N, 
                   all_melast = sum(val*val_w)/sum(val_w),
						 		   all_z = sum(val_z,na.rm=T)/sqrt(.N),
									 all_sig = signstars(sum(val_z,na.rm=T)/sqrt(.N)),
												  
									 dev_Neffects= length(which(!is.na(val[developed==1]))),
				           dev_melast = sum(val[developed==1]*val_w[developed==1])/sum(val_w[developed==1]),
									 dev_z = sum(val_z[developed==1])/sqrt(length(which(!is.na(val[developed==1])))),
									 dev_sig = signstars(sum(val_z[developed==1])/sqrt(length(which(!is.na(val[developed==1]))))),
									 
									 em_Neffects= length(which(!is.na(val[developed==0]))),
				           em_melast = sum(val[developed==0]*val_w[developed==0])/sum(val_w[developed==0]),
									 em_z = sum(val_z[developed==0])/sqrt(length(which(!is.na(val[developed==0])))),
									 em_sig = signstars(sum(val_z[developed==0])/sqrt(length(which(!is.na(val[developed==0])))))
									 ), by=c('variable')]

  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  return(tmp)
  })
  
iters = list(st=c('st', 'Short-term'), lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', 
        caption=tab(paste0(iter[2], ' elasticities by marketing mix instrument'))) %>% kable_styling() %>% 
        footnote(general=paste0('*p*<.001 (two-sided). ', estimnote)) %>% add_header_above(c(" " = 1, "All countries" = 4, "Developed countries" = 4, "Emerging countries" = 4)))
}

```

# Second-stage analysis

`r tab("Variable operationalization")`

Construct                  | Operationalization                                     | References
------------------------- | --------------------------------------------------------|----------
Appliance (versus electronics)| Dummy, equaling 1 for appliances (washing machines, microwaves and refrigerators), 0 for all other categories.
Category growth       | Log of a market's average growth rate in the observation period.^1^
Category concentration     | Log of Herfindahl index in a market.
Domestic versus foreign brand | Dummy, equaling 1 if a brand's headquarter is located in the focal country, 0 if not.
Price index | Log of a brand's average price (deflated sales value devided by the brand's sales volume over the observation period), indexed by the maximum price in a given category and country.
Brand equity               | Sales-based brand equity, obtained as a transformation of the brand-specific intercept from the market share attraction model, standardized by category. | Datta, Ailawadi, and van Heerde (2017)

*Note:* All continuous variables are logged and mean-centered before model estimation (except brand equity, which is only mean-centered as this variable can take on negative values). 

^1^ Geometric growth rate in a market, defined as the n-th's square root of the ratio of the total number of unit sales in a market in the last year over total number of unit sales in the first year (both years having 12 months of data). N equals to the number of years in the observation window.

```{r summarystats, echo=FALSE}

covars <- c('appliance', 'market_growth', 'herf', 'local_to_market', 'overall_prindex', 'sbbe_std', 'brandz')

tmp=data.table(elast)
nbrands=length(unique(tmp$brand))
nmarkets=length(unique(tmp$market_id))
tmp = unique(tmp, by = c('market_id','brand', 'emerging'))
nobs=nrow(tmp)

  
tmp=tmp[, lapply(.SD, function(x) c(min=min(x,na.rm=T), max=max(x,na.rm=T), mean=mean(x,na.rm=T),sd=sd(x,na.rm=T))), by = c('emerging'), .SDcols=c(covars)]
tmp[, var:=rep(c('min', 'max','mean', 'sd'),2)]
tmp=melt(tmp, id.var=c('emerging', 'var'))
tmp[, emerging_label:=ifelse(emerging==1, 'emerging', 'developed')]

dtf=dcast(tmp, variable~emerging_label+var)
setcolorder(dtf, c('variable', paste0(rep(c('emerging_', 'developed_'), each=4), rep(c('min', 'max', 'mean', 'sd'),2))))

setnames(dtf, gsub('emerging_', '', colnames(dtf)))
setnames(dtf, gsub('developed_', '', colnames(dtf)))

dtf=sanitize_table(dtf)

kable(dtf, digits=3,caption = tab(paste0('Summary statistics for covariates in second-stage analysis, split by a country\'s development status')),
      format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(general=paste0('Note: Summary statistics for variables in levels, computed on a sample of ', nbrands, ' unique brands in ', nmarkets, ' markets, totalling ', nobs, ' observations.')) %>%
  add_header_above(c(" " = 1, "Emerging countries" = 4, "Developed countries" = 4))
#c("striped", 'bordered')
```

# Analysis

```{r continue_with_selection, echo=FALSE}
elast_all=data.table(elast)
elast=elast[!is.na(country_of_origin)&!brand%in%c('unbranded')]
excluded_brands=setdiff(unique(elast_all$brand), unique(elast$brand))

```

On sample of `r length(unique(elast$brand))` unique brands (excluding `r paste0(my_capitalize(excluded_brands), collapse=', ')`).

```{r main_regs, echo = FALSE, results='asis'}

out1=regmodel(formula=c(main=form_main_model, interact=form_interact), dat=elast, model='lmer')
#out2=regmodel(formula=form_main_model, dat=elast, model='lmer')

#varsord = rep(ordered_vars,each=1)
#names(varsord) <- paste0(unlist(sanitize_table(data.frame(varsord))), ' elasticity')
names(ordered_vars) <- paste0(unlist(sanitize_table(data.frame(ordered_vars))), ' elasticity')

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

main = lapply(out1, function(x) {x$lt <- list(x$lt$main); x$st <- list(x$st$main); x})
interact = lapply(out1, function(x) {x$lt <- list(x$lt$interact); x$st <- list(x$st$interact); x})

# assemble all variables
#sink('../temp/test.html')

covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(main[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

cat("<P style='page-break-before: always'>")
printout(main, 'stlt', omit=NULL, title = tab('Regression with short- and long-term elasticities in a pooled sample of developed and emerging countries'), vars=ordered_vars, notes=notes_base, covlabels=covlabels, column.separate=rep(2, each=length(out1)),
         dep.var.labels.include=T, dep.var.labels=rep(c('short-term', 'long-term'),4),
         table.layout=c('-c#dm-t-s-n'))


covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(interact[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

cat("<P style='page-break-before: always'>")
printout(interact, 'stlt', omit=NULL, title = tab('Regression with short- and long-term elasticities in a pooled sample of developed and emerging countries, with interactions'), vars=ordered_vars, notes=notes_base, covlabels=covlabels, column.separate=rep(2, each=length(out1)),
         dep.var.labels.include=T, dep.var.labels=rep(c('short-term', 'long-term'),4),
         table.layout=c('-c#dm-t-s-n'))

#sink()

```

# Robustness checks

## Different variables to measure a country's development status

- Log of GDP per capita
- Log of Global Competitiveness Index
- Log of Human Development Index
- Socio-economic development of a country (score from principal component analysis on selected items from the Global Competitiveness Report, not logged as this score takes on negative values)

```{r robustness_regs, echo = FALSE, results='asis'}

modellist = lapply(c('emerging', 'ln_gci_00.03_gdppercap_s_mc', 'ln_gci_overall_s_mc', 'ln_hdi2010_mc', 'gcifactor_mc'), 
                   function(x) update.formula(update.formula(form_main_model, .~.-emerging), as.formula(paste0('.~. +', x))))

out1=regmodel(formula=modellist, dat=elast, model='lmer')

# assemble all variables
covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

varsord = rep(ordered_vars,each=1)
names(varsord) <- paste0(unlist(sanitize_table(data.frame(varsord))), ' elasticity')

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

#sink('../temp/test.html')
names(ordered_vars)=rename.fkt(ordered_vars)

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Regression with long-term elasticities on covariates and different indicators for a country\'s state of development'), vars=ordered_vars[1:2], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[1:2]], function(x) length(x$lt))))

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Regression with long-term elasticities on covariates and different indicators for a country\'s state of development'), vars=ordered_vars[3:4], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[3:4]], function(x) length(x$lt))))
#sink()
```

## Assessing robustness of brand equity metric

Replace Brand equity (SBBE) by dummy variable, equaling 1 if a brand is listed in either *BrandZ's Top 100 Most Valuable global brands (2010)*, or *BrandZ's Top 50 Most Valuable Chinese Brands (2011)*.

```{r robustness_regs_equity, echo = FALSE, results='asis'}

modellist = lapply(c('sbbe_std_mc', 'overall_ms_mc', 'brandz'), 
                   function(x) update.formula(update.formula(form_main_model, .~.-sbbe_std_mc), as.formula(paste0('.~. +', x))))

out1=regmodel(formula=modellist, dat=elast, model='lmer')

# assemble all variables
covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

varsord = rep(ordered_vars,each=1)
names(varsord) <- paste0(unlist(sanitize_table(data.frame(varsord))), ' elasticity')

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

#sink('../temp/test.html')
names(ordered_vars)=rename.fkt(ordered_vars)

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Regression with long-term elasticities on covariates and different indicators for brand equity'), vars=ordered_vars[1:2], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[1:2]], function(x) length(x$lt))))

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Regression with long-term elasticities on covariates and different indicators for brand equity'), vars=ordered_vars[3:4], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[3:4]], function(x) length(x$lt))))
#sink()
```


```{r report_pca, echo=FALSE,results='asis'} 

scores = fread('../output/pca_1comp_loadings.csv')
setnames(scores, c('variable', 'stdloading'))

scores[, variable_renamed:=sapply(variable, rename.fkt, dictionary='renaming_gci.txt')]
setcolorder(scores, c('variable_renamed', 'stdloading', 'variable'))
scores[, variable:=NULL]
setnames(scores, 'variable_renamed', 'Variable')
setnames(scores, 'stdloading', 'Standardized loading')

print(kable(scores, caption = tab(paste0('Standardized loadings on principal component for GCI metrics')),
      format='html', initial.zero = FALSE, digits = 3)%>%
        kable_styling())

```


```{r randomcombined_factorscore, echo = FALSE, results='asis'}
m1 = update.formula(form_modelbasis, form_extraregressor)
m1b = update.formula(m1, .~.+gcifactor_mc)

names(ordered_vars) <- paste0(unlist(sanitize_table(data.frame(ordered_vars))), ' elasticity')

out1=regmodel(formula=list(m1b), dat=elast, model='lmer')
carry_forward_model_for_plotting = out1

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

cat("<P style='page-break-before: always'>")

covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out1, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries, with GCI component score'), vars=ordered_vars,notes=notes_base, covlabels=covlabels,
         column.separate=unlist(lapply(out1, function(x) length(x$lt))))

# interaction model
cat("<P style='page-break-before: always'>")
out4=regmodel(formula=form_interact_gci, dat=elast, model='lmer')

covlabels=unlist(sanitize_table(data.frame(colnames(out4[[1]]$lt[[1]]@pp$X))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out4, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries, using interactions with the GCI component score'), vars=ordered_vars, notes=paste0(notes_base), covlabels=covlabels)

```


# Appendix

```{r reset, echo=FALSE,results='asis'}
tableno<<-0
figureno<<-0
cat("<P style='page-break-before: always'>")
  
```


```{r sample_origin, echo=FALSE, results='asis'}

cols =  c('country_of_origin')
tmp = elast[, list(.N), by = c('brand',cols)]
tmp = tmp[, list(nbrands=length(unique(brand)), all_brands=paste(stri_trans_totitle(brand[order(brand)]), collapse=', ')), by = cols]
tmp[country_of_origin==''|is.na(country_of_origin), country_of_origin := 'Country not available']
tmp[, country_of_origin:=my_capitalize(country_of_origin)]

setorderv(tmp, 'nbrands', order=-1L)
setcolorder(tmp, c('country_of_origin', 'nbrands', 'all_brands'))

tmp=sanitize_table(tmp)

kable(tmp, caption = tab('Country-of-origins for brands in sample, ordered by the number of brands from a given country', prefix ='A'),format='html') %>%
        kable_styling() %>% footnote(general=paste0('Note: Brand names listed alphabetically.'))

```


```{r elast_by_win, echo=F,results='asis', include=FALSE}

for (byvar in c('category', 'country')) {
  tmp=elast[!is.na(elastlt), list(elast = sum(elastlt*w_elastlt)/sum(w_elastlt)), by=c('variable', byvar)]
  setnames(tmp, byvar, 'byvar')
  
  tmp=dcast(tmp,byvar~variable,value.var='elast')
  setnames(tmp, 'byvar', byvar)
  setcolorder(tmp, c(byvar, ordered_vars))
  
  tmp=sanitize_table(tmp)
  setorderv(tmp, colnames(tmp)[1])
  
  cat("<P style='page-break-before: always'>")
  print(kable(tmp, digits=3, caption = tab(paste0('Long-term elasticities (by ', byvar, ')'), prefix='A'), format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(general=paste0('Note: ', estimnote, ' Reported by ', ifelse(byvar=='country', 'countries', 'categories'), ' in alphabetical order.')))
}
  
```	


```{r rq4_growth, echo=FALSE,results='asis'}
tmp=unique(elast, by = c('market_id')) # t-tests on growth rates

t_tests <- lapply(unique(elast$category), function(var) {
    tmpdat = tmp[category == var]
    teststat=t.test(tmpdat[country_class=='hinc']$market_growth, tmpdat[country_class=='linc']$market_growth)
    
    tabl = data.frame(category=var, mean1=teststat$estimate[1], mean2=teststat$estimate[2], t=teststat$statistic, p=teststat$p.value)
                
    return(list(summary=tabl))
})

out=rbindlist(lapply(t_tests, function(x) x$summary))

percent <- function(x, digits = 1, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}

out[, ':=' (mean1=percent(mean1-1), mean2=percent(mean2-1))]
out[, category:=as.character(category)]
out=sanitize_table(out)
setorder(out, Category)
setnames(out, 'mean1', 'developed countries')
setnames(out, 'mean2', 'emerging countries')
cat("<P style='page-break-before: always'>")
kable(out, format='html',caption = tab('Average category growth rates for developed and emerging countries',prefix='A'),digits=3) %>% kable_styling() %>% footnote(general=paste0('Note: Table reports average category growth rates, and the results of a t-test of statistical significance of the difference in growth rates between developed and emerging countries. Categories are ordered alphabetically.'))
  
```

```{r VIFS, echo=FALSE,results='asis'}

m1 = ~1+ appliance + ln_market_growth_mc + ln_herf_mc + local_to_market  + ln_overall_prindex_mc 

m<-lm(update(elast~., m1), data=elast[variable=='llen'])

frame1=data.frame(vif(m))
colnames(frame1) <- c('VIF')
frame1$variable=rownames(frame1)
rownames(frame1)<-NULL
frame1=frame1[, c('variable','VIF')]
frame1=sanitize_table(frame1)
cat("<P style='page-break-before: always'>")
kable(frame1,format='html', caption = tab('VIFs in a model without interactions', prefix='A'))%>% kable_styling() %>% footnote(general=paste0('Note: VIFs calculated in regression models using the variables listed above (i.e., excluding brand, category, and country effects).'))

```

```{r elasts_full, echo=F,results='asis'}

cat("<P style='page-break-before: always'>")

  sigvalue = .1 # .1-level of significance
  zval = qnorm(1-sigvalue/2)

  out = lapply(list(st=c('elast', 'z_elast', 'w_elast'), lt = c('elastlt','z_elastlt','w_elastlt')), function(obj) {
               
    tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), val_z=get(obj[2]), val_w=get(obj[3]))]
    
    tmp=tmp[, list(Neffects=.N, median_elast = median(val), 
												  melast = sum(val*val_w)/sum(val_w),
												  perc_positive = length(which(val_z>=(zval)))/.N, 
												  perc_null = length(which(abs(val_z)<zval))/.N, 
												  perc_negative = length(which(val_z<=(-zval)))/.N), by=c('variable')]
    
  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  return(tmp)
  })
  
iters = list(st=c('st', 'Short-term'), lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', 
        caption=tab(paste0(iter[2], ' elasticities by marketing mix instrument'),prefix='A')) %>% kable_styling() %>% 
        footnote(general=paste0('Note: Table reports ', tolower(iter[2]), ' elasticities. ', estimnote, ' Significance tested at p<',sigvalue, '.')))
}

```

# Estimation details

## Market share attraction model

Elasticities estimated using a market share attraction model (MCI), with

* four marketing mix instruments:
     + llen = line length (number of SKUs)
     + wpswdst = distribution (weighted using past sales in previous three periods)
     + price = rwpspr (deflated using a country's CPI, weighted using past sales in previous three periods)
     + novelty = nov6sh (number of SKUs introduced in past six periods, expressed as a share of total SKUs sold in a given period)
  
* endogeneity controls using Gaussian Copulas (tested at p<.1; removed if n.s.)
* lagged market share to model dynamics
* brand-specific trend
* brand-specific quarterly dummies

Elasticities and corresponding standard errors calculated using the Delta rule.

## Estimation data set

- Number of markets: `r length(unique(elast_all$market_id))`.
- Number of brands: `r nrow(elast_all[, .N, by = c('market_id', 'brand')])`.
- Number of unique brands: `r nrow(elast_all[, .N, by = c('brand')])`.
- Included countries (`r length(unique(elast_all$country))`): `r paste0(unique(elast_all$country),collapse = ', ')`.
- Included categories (`r length(unique(elast_all$category))`): `r paste0(unique(elast_all$category),collapse = ', ')`.

```{r overview2, echo=FALSE, results='asis'}
tmp = elast_all[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
#print(xtable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data')), scalebox='0.6',type='html',caption.placement='top')
tabl=sanitize_table(tabl)
setorder(tabl, Category)
kable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data', prefix='A'))

```


```{r sample_overview, echo=FALSE, results='asis'}
#, headquarter_region=unique(country_of_origin)
tmp=elast[, list(active_in_countries=length(unique(country)), active_in_categories=length(unique(category)), headquarter_location=unique(country_of_origin)), by = c('brand')]
setorderv(tmp, c('active_in_countries','active_in_categories', 'brand'),order=-1L)

tmp[, ':=' (brand=stri_trans_totitle(brand), headquarter_location=stri_trans_totitle(headquarter_location))]#, #headquarter_region=stri_trans_totitle(headquarter_region))]
tmp=sanitize_table(tmp)


kable(tmp, caption = tab('Overview of selected brands, ordered by the number of countries and categories it is active in', prefix ='A'))
```

