---
title: "GfK Singapore - Results"
output:
  html_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(stargazer)
library(knitr)
require(xtable)
library(lme4)
library(car)
library(kableExtra)
library(stringi)


options(xtable.comment = FALSE)

# Load data
  #elast <- fread('../externals/elast_results_MCI_wlag_wotrend.csv')
  elast <- fread('../externals/elast_results_MCI_wolag_trend.csv')

# Load auxilary functions
  source('proc_auxilary.R')

# load extra variables
  hdi <- fread('../temp/hdi.csv')
# change taiwan (reported value from China is not reliable)
  hdi[, hdi2010:=ifelse(country=='taiwan', mean(hdi2010[country%in%c('thailand', 'china')]), hdi2010)]
# Load GDP
  gdp <- fread('../temp/gdp.csv')
# Merge
  setkey(hdi, country)
  setkey(elast, country)
  elast[hdi, hdi2010:=i.hdi2010]
  setkey(gdp, country)
  elast[gdp, gdppercap2010:=i.gdppercap2010]

  elast[, country_of_origin_recode := ifelse(country_of_origin%in%c('local','asian_other'), 'asian', country_of_origin)]
  
  # elast asian devel vs. not
  elast[, region_of_origin:=country_of_origin_recode]
  elast[region_of_origin=='asian'& country_class=='hinc', region_of_origin := 'asian-high']
  elast[region_of_origin=='asian'& country_class=='linc', region_of_origin := 'asian-low']
  
  elast[, appliance:=necessity]
  
  
  elast[, developed:=0]
  elast[country%in%c('australia', 'singapore', 'japan', 'new zealand', 'hong kong', 'south korea'), developed := 1]


# take natural log of variables
vars=c('herf','c3','c5','market_growth','hdi2010','gdppercap2010', 'ncat_in_country', 'ncountry_in_category')

for (var in vars) {
  elast[, (paste0('ln_', var)):=log(get(var))]
  
}

# grand-mean centering by variable (llen, etc.) for all explanatory (continuous) variables
for (var in unique(drop(unlist(lapply(vars, grep, colnames(elast), value=T))))) {
  elast[, (paste0(var, '_mc')):=get(var)-mean(get(var)), by = c('variable')]
  }
  
# focal dummies: local_to_market, western (versus asian)

#
elast[, worldbank := '']
elast[country%in%c('india','indonesia', 'vietnam', 'philippines'), worldbank:='lowermid']
elast[country%in%c('china', 'malaysia','thailand'), worldbank:='uppermid']
elast[worldbank=='', worldbank:='high']

options(knitr.kable.NA = '')

### brand selection for analysis
#elast=elast[globalbrand==T] # global brands (active in >=3 countries) only

#elast=elast[ncountries>=2]

source('proc_rename.R')

```

```{r devel, echo = FALSE}
tmp=unique(elast, by='country')[, c('country','gdppercap2010','hdi2010'),with=F]
setorderv(tmp, c('gdppercap2010'), order=-1L)

kable(tmp, format='html', caption=tab('Development indicators for countries in sample')) %>%
        kable_styling() %>% footnote(general='Countries ranked by GDP per capita.', alphabet=c("GDP per capita in current USD, 2010 data. Provided by World Bank (NY.GDP.PCAP.CD) for all countries except Taiwan. Data for Taiwan obtained from Datastream (WGDPPEAA~USD).", "Human Development Index (HDI), 2010 data. Taiwan's HDI has been imputed as the mean HDI of Thailand and China."))

```

```{r table2_category_overview, echo = FALSE}
tmp=data.table(elast)
tmp[, ncountries:=length(unique(country)),by=c('category')]

tmp=tmp[, list(overall_ms=mean(overall_ms), ncountries=mean(ncountries)), by = c('category', 'appliance', 'brand')]

setorderv(tmp, c('category', 'appliance', 'overall_ms'), order=-1L)
tmp[!brand%in%c('unbranded','local'), rank:=1:.N, by = c('category')]
tmp[, brand_include:= rank%in%1:5]

sort_alpha <- function(x) return(x[order(x)])

tmp=tmp[brand_include==T, list(cattype=ifelse(unique(appliance)==1, 'Appliance', 'Electronics'), ncountries=unique(ncountries), exemplary_brand_names=paste0(sort_alpha(stri_trans_totitle(unique(brand))), collapse=', ')), by='category']
setorder(tmp, category)

kable(tmp, format='html', caption=tab('Category overview')) %>%
        kable_styling() %>% footnote(general='Categories ranked by alphabet. Exemplary brand names displayed for Top 5 brands in terms of average market share across countries, in alphabetic order.')

```

```{r table3_varoperation, echo=F}

tmp = data.table(variable=c('line length', 'etc.'))
kable(tmp, caption=tab('Variable operationalization for market share attraction model'))

```

(still to be completed)

```{r elast_means, echo = FALSE, results='asis'}

m1 = ~1
m2 = ~-1+as.factor(country_class)
out1=regmodel(formula=list(m1,m2), dat=elast, model='lm')

printout(out1, 'lt', omit=NULL, title = tab('long-term elasticities'), vars=NULL)

```
## Elasticities

```{r elast_ov, echo = FALSE, results='asis'}
  .vars=c('llen','wpswdst','rwpspr','nov6sh')
	
  zval=qnorm(.95) # zval for .1-level of significance

  
  tmp=elast[!is.na(elastlt), list(welast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  Neffects= .N, 
												  perccorrectsign = length(which(elastlt/elastlt_se>=ifelse(variable=='rwpspr', -1, 1)*zval))/.N,
												  welast_emerging = sum(elastlt[developed==0]/elastlt_se[developed==0])/sum(1/elastlt_se[developed==0]),
												   welast_developed = sum(elastlt[developed==1]/elastlt_se[developed==1])/sum(1/elastlt_se[developed==1])), by=c('variable')]
  
	kable(tmp[match(.vars, variable)], digits=3, caption = tab('Long-term elasticities by variable, significance tested at p<.1 (|z| >= 1.64)'))

```
```{r elast_hist, echo=F}

elast[, obs_rank:=rank(elastlt), by = c('variable', 'developed')]
setorder(elast,variable, developed, obs_rank)
elast[, ptile := obs_rank/max(obs_rank), by = c('variable', 'developed')]
elast[, group:=cut(ptile, breaks=c(0,.25, .5, .75,1), labels=c('Q1', 'Q2', 'Q3', 'Q4'))]

tmp=elast[, list(qmeans=mean(elastlt)),by=c('variable', 'developed','group')]

for (.var in unique(elast$variable)){
p<-ggplot(tmp[variable==.var], aes(x=group, y=qmeans, fill=ifelse(developed==1, 'developed', 'emerging'))) + theme_bw() + geom_bar(position=position_dodge(), stat="identity") +ggtitle(fig('.var')) +scale_fill_grey() + labs(title = paste0("Mean long-term ", rename.fkt(.var), " elasticities per quartile"))+guides(fill=guide_legend("Development status")) +xlab("Quartiles") + 
           ylab("Elasticity")
print(p)
}

```

## Variable operationalization

Variable name             | Construct                  | Operationalization
------------------------- | -------------------------- | ------------------------------------------------------------
ln_gdppercap2010          | Degree of development      | Log of GDP per capita, measured in 2010
necessity                 | Necessary goods            | Dummy for 'necessary' goods, equaling 1 for washing machines, microwaves and refridgerators
ln_market_growth          | Category growth rate       | Log of a market's average growth rate in the observation period (geometric average)
ln_herf                   | Category concentration     | Log of Herfindahl index
local_to_market           | Local versus foreign brand | Dummy, equaling 1 if brand is local to a market, or not (0 = foreign)
western_brand             | Western versus Asian brand | Dummy variable, equaling 1 if brand is headquartered in North America or Europe (0 for Asia).
ln_ncat_in_country        | Cross-country presence     | Number of categories a brand is active in, within a specific category
ln_ncountry_in_category   | Cross-category presence    | Number of categories a brand is active in, within a specific country

All continuous variables are mean-centered before model estimation.



```{r continue, echo=FALSE}
elast=elast[globalbrand==T] # global brands (active in >=3 countries) only
```

# Analysis sample

We continue our analysis with global brands (`r length(unique(elast$brand))` unique brands) that are active in at least 3 out of the 14 countries in our data. Later on, we can revisit this decision (depends on input of RA who is coding headquarter locations for the complete set of brands).

```{r sample_overview, echo=FALSE, results='asis'}

tmp=elast[, list(active_in_countries=length(unique(country)), active_in_categories=length(unique(category)), headquarter_location=unique(global_country), headquarter_region=unique(country_of_origin_recode)), by = c('brand')]
setorderv(tmp, c('active_in_countries','active_in_categories'),order=-1L)
kable(tmp, caption = tab('Overview of selected brands, ordered by the number of countries and categories it is active in'))
```



# Results

## with log GDP

Model with weights (equal to the inverse of an elasticity's standard error), and random effects for countries, categories, and brands.

- First model with main effects only
- Second model with interactions between economic development (log GDP), and the remaining variables.

```{r randomcombined1, echo = FALSE, results='asis'}

m1 = ~1+ln_gdppercap2010_mc + (1|brand) + (1|category) + (1|country)+ necessity + ln_market_growth_mc + ln_herf_mc + local_to_market + western_brand + ln_ncat_in_country_mc + ln_ncountry_in_category_mc

interact1 = . ~ . + necessity*ln_gdppercap2010_mc + ln_market_growth_mc*ln_gdppercap2010_mc +
  local_to_market*ln_gdppercap2010_mc + western_brand*ln_gdppercap2010_mc +
  ln_herf_mc*ln_gdppercap2010_mc + ln_ncat_in_country_mc*ln_gdppercap2010_mc + ln_ncountry_in_category_mc*ln_gdppercap2010_mc

m2=update(m1, interact1)

out1=regmodel(formula=m1, dat=elast, model='lmer')

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('DV: long-term elasticities'), vars=NULL)

cat("<P style='page-break-before: always'>")
out2=regmodel(formula=m2, dat=elast, model='lmer')
printout(out2, 'lt', omit=NULL, title = tab('DV: long-term elasticities, with interactions'), vars=NULL)

```


## with country dummies

Drop random effects for countries, replace by dummy variables.

```{r randomcombined4, echo = FALSE, results='asis'}

m1 = ~1+ (1|brand) + (1|category) + as.factor(country) + necessity + ln_market_growth_mc + ln_herf_mc + local_to_market + western_brand + ln_ncat_in_country_mc + ln_ncountry_in_category_mc

out1=regmodel(formula=m1, dat=elast, model='lmer')

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('long-term elasticities'), vars=NULL)


```

# Appendix

## VIFs

estimating an auxilary regression (elast for llen on variables, without brand/category/country effects), then computing VIFs.

```{r VIFS, echo=FALSE}
m1 = ~1+ln_gdppercap2010_mc + necessity + ln_market_growth_mc + ln_herf_mc + local_to_market + western_brand + ln_ncat_in_country_mc + ln_ncountry_in_category_mc

interact1 = . ~ . + necessity*ln_gdppercap2010_mc + ln_market_growth_mc*ln_gdppercap2010_mc +
  local_to_market*ln_gdppercap2010_mc + western_brand*ln_gdppercap2010_mc

m2=update(m1, interact1)

m<-lm(update(elast~., m1), data=elast[variable=='llen'])
m2<-lm(update(elast~., m2), data=elast[variable=='llen'])
cat("<P style='page-break-before: always'>")

kable(data.frame(vif(m)), caption = tab('VIFs in a model without interactions'))
kable(data.frame(vif(m2)), caption = tab('VIFs in a model with interactions'))


```

# Elasticities

## Short-term
```{r shorterm, echo=F}
  .vars=c('llen','wpswdst','rwpspr','nov6sh')
	
  zval=qnorm(.95)
  
	tmp=elast[!is.na(elast), list(median_elast = median(elast), 
												  w_elast = sum(elast/elast_se)/sum(1/elast_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elast/elast_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elast/elast_se)<zval))/.N, 
												  perc_negative = length(which(elast/elast_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], caption = tab('Short-term elasticities by variable'))
```	

## Long-term
```{r elast_lt, echo = FALSE, results='asis'}
  .vars=c('llen','wpswdst','rwpspr','nov6sh')
	
  zval=qnorm(.95) # zval for .1-level of significance

  tmp=elast[!is.na(elastlt), list(median_elast = median(elastlt), 
												  w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elastlt/elastlt_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elastlt/elastlt_se)<zval))/.N, 
												  perc_negative = length(which(elastlt/elastlt_se<=(-zval)))/.N), by=c('variable')]
	kable(tmp[match(.vars, variable)], digits=3, caption = tab('Long-term elasticities by variable, significance tested at p<.1 (|z| >= 1.64)'))

```


Estimated using a market share attraction model (MCI), with

* four marketing mix instruments:
     + llen = line length (number of SKUs)
     + wpswdst = distribution (weighted using past sales in previous three periods)
     + price = rwpspr (deflated using a country's CPI, weighted using past sales in previous three periods)
     + novelty = nov6sh (number of SKUs introduced in past six periods, expressed as a share of total SKUs sold in a given period)
  
* endogeneity controls using Gaussian Copulas (tested at p<.1; removed if n.s.)
* lagged market share to model dynamics
* brand-specific trend
* brand-specific quarterly dummies


Elasticities and corresponding standard errors calculated using the Delta rule.


# Estimation data set

- Number of markets: `r length(unique(elast$market_id))`.
- Number of brands: `r nrow(elast[, .N, by = c('market_id', 'brand')])`.
- Number of unique brands: `r nrow(elast[, .N, by = c('brand')])`.
- Included countries (`r length(unique(elast$country))`): `r paste0(unique(elast$country),collapse = ', ')`.
- Included categories (`r length(unique(elast$category))`): `r paste0(unique(elast$category),collapse = ', ')`.



```{r overview2, echo=FALSE, results='asis'}
tmp = elast[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
#print(xtable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data')), scalebox='0.6',type='html',caption.placement='top')

kable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data'))

```


## category lifecycles

```{r rq4_growth, echo=FALSE}
tmp=unique(elast, by = c('market_id')) # t-tests on growth rates

t_tests <- lapply(unique(elast$category), function(var) {
    tmpdat = tmp[category == var]
    teststat=t.test(tmpdat[country_class=='hinc']$market_growth, tmpdat[country_class=='linc']$market_growth)
    
    tabl = data.frame(category=var, mean1=teststat$estimate[1], mean2=teststat$estimate[2], t=teststat$statistic, p=teststat$p.value)
                
    return(list(summary=tabl))
})

out=rbindlist(lapply(t_tests, function(x) x$summary))

setnames(out, 'mean1', 'high-income')
setnames(out, 'mean2', 'low-income')
out[, category:=as.character(category)]
setorder(out, category)

kable(out, caption = tab('Average category growth rates for high-income and low-income countries, and t-test for significance'),digits=3)

```
