---
title: "GfK Singapore - Results"
output:
  html_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(plyr)
#library(psych)

libs_to_load <- c('data.table', 'stargazer', 'knitr', 'xtable', 'lme4', 'car', 'kableExtra', 'stringi', 'ggplot2')
for (lib in libs_to_load) eval(parse(text=paste('library(', lib, ')')))

options(xtable.comment = FALSE)
options(knitr.kable.NA = '')

# Load data
  #elast <- fread('../externals/elast_results_MCI_wlag_wotrend.csv')
  elast <- fread('../externals/elast_results_MCI_wolag_trend.csv')

# Load auxilary functions
  source('proc_auxilary.R')
  source('proc_rename.R')

# Preclean data
  source('preclean.R')
  
# set order of variables to appear in figures and tables
ordered_vars = c('rwpspr', 'wpswdst','llen','nov6sh')

# fix 'standard' covariates
form_random_component = .~1+ (1|brand) + (1|category) + (1|country)
form_random_component_FE = .~1+ (1|brand) + (1|category) + as.factor(country)
form_std = .~. + appliance + ln_market_growth_mc + ln_herf_mc + local_to_market + ln_overall_prindex_mc

form_interact = ~1+ (1|brand) + (1|category) + (1|country) + emerging + appliance + I(appliance*emerging) + ln_market_growth_mc + I(ln_market_growth_mc*emerging) + ln_herf_mc + I(ln_herf_mc*emerging) + local_to_market + I(local_to_market*emerging) + ln_overall_prindex_mc + I(ln_overall_prindex_mc*emerging) + sbbe_std_mc + I(sbbe_std_mc*emerging)

form_interact_gci = ~1+ (1|brand) + (1|category) + (1|country) + gcifactor_mc + appliance + I(appliance*gcifactor_mc) + ln_market_growth_mc + I(ln_market_growth_mc*gcifactor_mc) + ln_herf_mc + I(ln_herf_mc*gcifactor_mc) + local_to_market + I(local_to_market*gcifactor_mc) + ln_overall_prindex_mc + I(ln_overall_prindex_mc*gcifactor_mc) + sbbe_std_mc + I(sbbe_std_mc*gcifactor_mc)


# choice for main 'brand strength' variable
form_modelbasis = update.formula(form_random_component, form_std)
form_extraregressor = .~. + sbbe_std_mc

winsor_p=.05

#estimtype = 'winsor-onesided'
estimtype = 'weighted'
#estimtype = 'winsor-twosided'

# apply winsorization
# 1-sided
if (estimtype=='winsor-onesided') {
  
  for (.var in c('elast', 'elastlt')) {
    elast[!is.na(get(.var)), (.var) := winsor_onesided(get(.var), fraction=winsor_p, ifelse(variable=='rwpspr', 'right','left')), by=c('variable')]
    elast[!is.na(get(.var)), paste0('w_', .var) := 1]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities have been winsorized at ', winsor_p*100, '%, left-sided for all variables except price.')
  
}

# 2-sided
if (estimtype=='winsor-twosided') {
  
  for (.var in c('elast', 'elastlt')) {
    elast[!is.na(get(.var)), (.var) := winsor_onesided(get(.var), fraction=winsor_p, side='both'), by=c('variable')]
    elast[!is.na(get(.var)), paste0('w_', .var) := 1]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities have been winsorized at ', winsor_p*100, '%, two-sided.')
  
}

if (estimtype=='weighted') {
  
  for (.var in c('elast', 'elastlt')) {

    elast[!is.na(get(.var)), paste0('w_', .var) := 1/get(paste0(.var, '_se'))]
    elast[!is.na(get(.var)), paste0('z_', .var) := get(.var)/get(paste0(.var, '_se'))]
  }
   
      estimnote = paste0('Elasticities are weighted by inverse standard errors.')
  
}
```

# Data

```{r table1_countries, echo = FALSE}
tmp=unique(elast, by='country')[, c('country','gci_00.03_gdppercap_s','hdi2010','gci_overall_s', 'developed'),with=F]
setorderv(tmp, c('developed', 'gci_00.03_gdppercap_s'), order=-1L)
first_emerging=match(0,tmp$developed)
tmp[, developed:=NULL]

kable(sanitize_table(tmp), format='html', initial.zero = FALSE, caption=tab('Development indicators for countries in sample')) %>%
        kable_styling() %>% footnote(general='Countries ranked by GDP per capita.', alphabet=c("GDP per capita in current USD, 2010 data, IMF World Economic Outlook Database (April 2010). Extracted from Global Competitiveness Report 2010, available at https://www.weforum.org/reports/global-competitiveness-report-2010-2011.", "Human Development Index (HDI), 2010 data, obtained from UN Development Programme (http://hdr.undp.org/en/content/human-development-index-hdi). Taiwan's HDI has been imputed as the mean HDI of Thailand and China.", "Global Competitiveness Index measures national competitiveness, capturing microeconomic and macroeconomic foundations of national competitiveness. Metric available at https://www.weforum.org/reports/global-competitiveness-report-2010-2011.")) %>%
  group_rows("Developed economies", 1, first_emerging-1) %>%
  group_rows("Emerging economies", first_emerging, 14)

```

```{r table2_category_overview, echo = FALSE}
tmp=data.table(elast)
tmp[, ncountries:=length(unique(country)),by=c('category')]

tmp=tmp[, list(overall_ms=mean(overall_ms), ncountries=mean(ncountries)), by = c('category', 'appliance', 'brand')]

setorderv(tmp, c('category', 'appliance', 'overall_ms'), order=-1L)
tmp[!brand%in%c('unbranded','local'), rank:=1:.N, by = c('category')]
tmp[, brand_include:= rank%in%1:5]


tmp=tmp[, list(cattype=ifelse(unique(appliance)==1, 'Appliance', 'Electronics'), ncountries=unique(ncountries), nbrands=length(unique(brand)), exemplary_brand_names=paste0((my_capitalize(unique(brand[brand_include==T]))), collapse=', ')), by='category']
tmp=sanitize_table(tmp)

try(setorder(tmp, Category),silent=T)

kable(tmp, format='html', caption=tab('Category overview')) %>%
        kable_styling() %>% footnote(general='Categories shown in alphabetical order. Top 5 brands are determined on the basis of their average volume share across countries, and are listed in decreasing order of their market shares.')

```

# Market share model

`r tab('Variable operationalization for market share attraction model')`


Variable             | Operationalization
-------------------- | ------------------------------------------------------------------
Market share         | Unit sales for brand *i* in period *t*, devided by total unit sales in period *t* in a market.
Price                | Sales-weighted^1^ average of each SKU's price sold by brand *i* in period *t*, expressed in local currency and adjusted by a country's consumer price index^2^.
Distribution         | Sales-weighted^1^ distribution of each of brand *i*'s SKUs' store-weighted distribution in period *t* (0 = no market coverage, 100 = full market coverage).
Line length          | Number of unique SKUs sold by brand *i* in period *t*.
New product activity | Number of SKUs introduced by brand *i* in a rolling window of 6 months (*t-5*, *t-4*, *...*, *t*), expressed as a share of the total number of unique SKUs sold by brand *i* over the same period.

Notes:

^1^ Weights equal to a SKU's unit sales in the most recent quarter (t-2, t-1, t).

^2^ Consumer price index obtained from Thomson Reuters Datastream.

```{r elasticities_overview, echo = FALSE, results='asis'}
  sigvalue = .1 # .1-level of significance
  
  zval = qnorm(1-sigvalue/2)

  out = lapply(list(st=c('elast', 'w_elast', 'z_elast'), lt = c('elastlt','w_elastlt', 'z_elastlt')), function(obj) {
               
    tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), 
                                             val_w=get(obj[2]),
                                             val_z=get(obj[3]))]
    
    tmp=tmp[, list(Neffects= .N, 
                   all_melast = sum(val*val_w)/sum(val_w),
						 		   all_z = sum(val_z,na.rm=T)/sqrt(.N),
									 all_sig = signstars(sum(val_z,na.rm=T)/sqrt(.N)),
												  
									 dev_Neffects= length(which(!is.na(val[developed==1]))),
				           dev_melast = sum(val[developed==1]*val_w[developed==1])/sum(val_w[developed==1]),
									 dev_z = sum(val_z[developed==1])/sqrt(length(which(!is.na(val[developed==1])))),
									 dev_sig = signstars(sum(val_z[developed==1])/sqrt(length(which(!is.na(val[developed==1]))))),
									 
									 em_Neffects= length(which(!is.na(val[developed==0]))),
				           em_melast = sum(val[developed==0]*val_w[developed==0])/sum(val_w[developed==0]),
									 em_z = sum(val_z[developed==0])/sqrt(length(which(!is.na(val[developed==0])))),
									 em_sig = signstars(sum(val_z[developed==0])/sqrt(length(which(!is.na(val[developed==0])))))
									 ), by=c('variable')]

  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  return(tmp)
  })
  
iters = list(st=c('st', 'Short-term'), lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', 
        caption=tab(paste0(iter[2], ' elasticities by marketing mix instrument'))) %>% kable_styling() %>% 
        footnote(general=paste0('*p*<.001 (two-sided). ', estimnote)) %>% add_header_above(c(" " = 1, "All countries" = 4, "Developed countries" = 4, "Emerging countries" = 4)))
}

```

# Second-stage analysis

`r tab("Variable operationalization")`

Construct                  | Operationalization                                     | References
------------------------- | --------------------------------------------------------|----------
Appliance (versus electronics)| Dummy, equaling 1 for appliances (washing machines, microwaves and refrigerators), 0 for all other categories.
Category growth       | Log of a market's average growth rate in the observation period.^2^
Category concentration     | Log of Herfindahl index in a market.
Domestic versus foreign brand | Dummy, equaling 1 if a brand's headquarter is located in the focal country, 0 if not.
Brand equity               | Sales-based brand equity, obtained as a transformation of the brand-specific intercept from the market share attraction model; (a) short-term, (b) long-term, (c) standardized by category.    | Datta, Ailawadi, and van Heerde (2017)
Brand-level market share  | Log of a brand's average market share in a market over the observation period.
Price index | Log of a brand's average price (deflated sales value devided by the brand's sales volume over the observation period), indexed by the maximum price in a given category and country.
Global brand (BrandZ) | Dummy, equaling 1 if a brand is listed in either *BrandZ's Top 100 Most Valuable global brands (2010)*, or *BrandZ's Top 50 Most Valuable Chinese Brands (2011)* | ...
Global competitiveness index | Overall score for a country's competitiveness^1^ | Steenkamp and Geyskens (2014)
Subindex basic requirements | Score based on a country's development status determined by institutions, infrastructure, macroeconomic environment, and health & primary education^1^ | ...
Subindex efficiency enhancers | Score based on a country's development status determined by higher education & training, goods market efficiency, labor market efficiency, financial market development, technological readiness and market size^1^ | ...
Subindex innovation and sophistication factors | Score based on a country's development status determined by business sophistication and innovation^1^ | ...

*Note:* All continuous variables are logged and mean-centered before model estimation (except brand equity, which is only mean-centered as this variable can take on negative values). 

^1^ Based on the World Economic Forum's Global Competitiveness Report (2010/2011, available at https://www.weforum.org/reports/global-competitiveness-report-2010-2011)
^2^ Geometric growth rate in a market, defined as the n-th's square root of the ratio of the total number of unit sales in a market in the last year over total number of unit sales in the first year (both years having 12 months of data). N equals to the number of years in the observation window.

```{r summarystats, echo=FALSE}

covars <- c('appliance', 'market_growth', 'herf', 'local_to_market', 'sbbe_std', 'sbbe', 'sbbelt', 'overall_ms', 'overall_prindex', 'brandz')

tmp=data.table(elast)
nbrands=length(unique(tmp$brand))
nmarkets=length(unique(tmp$market_id))
tmp = unique(tmp, by = c('market_id','brand', 'emerging'))
nobs=nrow(tmp)

  
tmp=tmp[, lapply(.SD, function(x) c(min=min(x,na.rm=T), max=max(x,na.rm=T), mean=mean(x,na.rm=T),sd=sd(x,na.rm=T))), by = c('emerging'), .SDcols=c(covars)]
tmp[, var:=rep(c('min', 'max','mean', 'sd'),2)]
tmp=melt(tmp, id.var=c('emerging', 'var'))
tmp[, emerging_label:=ifelse(emerging==1, 'emerging', 'developed')]

dtf=dcast(tmp, variable~emerging_label+var)
setcolorder(dtf, c('variable', paste0(rep(c('emerging_', 'developed_'), each=4), rep(c('min', 'max', 'mean', 'sd'),2))))

setnames(dtf, gsub('emerging_', '', colnames(dtf)))
setnames(dtf, gsub('developed_', '', colnames(dtf)))

# to b de done.

dtf=sanitize_table(dtf)

kable(dtf, digits=3,caption = tab(paste0('Summary statistics for covariates in second-stage analysis, split by a country\'s development status')),
      format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(general=paste0('Note: Summary statistics for variables in levels, computed on a sample of ', nbrands, ' unique brands in ', nmarkets, ' markets, totalling ', nobs, ' observations.')) %>%
  add_header_above(c(" " = 1, "Emerging countries" = 4, "Developed countries" = 4))
#c("striped", 'bordered')
```

# Analysis

```{r continue_with_selection, echo=FALSE}
elast_all=data.table(elast)
elast=elast[!is.na(country_of_origin)&!brand%in%c('unbranded')]
excluded_brands=setdiff(unique(elast_all$brand), unique(elast$brand))

```

On sample of `r length(unique(elast$brand))` unique brands (excluding `r paste0(my_capitalize(excluded_brands), collapse=', ')`).

## Model selection 

```{r modelselection, echo = FALSE, results='asis'}

modellist = lapply(c('sbbe_std_mc', 'sbbe_mc', 'sbbelt_mc', 'ln_overall_ms_mc', 'brandz'), 
                   function(x) update.formula(update.formula(form_modelbasis, .~.+emerging), as.formula(paste0('.~. +', x))))

out1=regmodel(formula=modellist, dat=elast, model='lmer')

# assemble all variables
covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

varsord = rep(ordered_vars,each=1)
names(varsord) <- paste0(unlist(sanitize_table(data.frame(varsord))), ' elasticity')

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

#sink('../temp/test.html')
names(ordered_vars)=rename.fkt(ordered_vars)

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Model selection: regression with long-term elasticities in a pooled sample of developed and emerging countries'), vars=ordered_vars[1:2], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[1:2]], function(x) length(x$lt))))

cat("<P style='page-break-before: always'>")
printout(out1, 'lt', omit=NULL, title = tab('Model selection: regression with long-term elasticities in a pooled sample of developed and emerging countries'), vars=ordered_vars[3:4], notes=notes_base, covlabels=covlabels, column.separate=unlist(lapply(out1[ordered_vars[3:4]], function(x) length(x$lt))))

#sink()
```

```{r randomcombined1, echo = FALSE, results='asis'}
m1 = update.formula(form_modelbasis, form_extraregressor)
m1b = update.formula(m1, .~.+emerging)

names(ordered_vars) <- paste0(unlist(sanitize_table(data.frame(ordered_vars))), ' elasticity')

out1=regmodel(formula=list(m1b), dat=elast, model='lmer')
carry_forward_model_for_plotting = out1

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

cat("<P style='page-break-before: always'>")

covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out1, 'st', omit=NULL, title = tab('DV: short-term elasticities, pooled sample of developed and emerging countries'), vars=ordered_vars,notes=gsub('long[-]term', 'short-term', notes_base), covlabels=covlabels,
         column.separate=unlist(lapply(out1, function(x) length(x$lt))))


cat("<P style='page-break-before: always'>")

printout(out1, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries'), vars=ordered_vars,notes=notes_base, covlabels=covlabels,
         column.separate=unlist(lapply(out1, function(x) length(x$lt))))

# interaction model
m2 = form_interact

cat("<P style='page-break-before: always'>")
out4=regmodel(formula=m2, dat=elast, model='lmer')

covlabels=unlist(sanitize_table(data.frame(colnames(out4[[1]]$lt[[1]]@pp$X))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out4, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries with interactions'), vars=ordered_vars, notes=paste0(notes_base), covlabels=covlabels)

```

```{r ploteffects, echo = FALSE, include = FALSE}
names(carry_forward_model_for_plotting)
j=1

outmod=lapply(seq(along=carry_forward_model_for_plotting), function(mod) {
  
  predmodel = carry_forward_model_for_plotting[[mod]]$lt[[j]]
  preddat = data.table(predmodel@frame)
  preddat[, predicted:=predict(predmodel)]
  tmp=preddat[, list(meanpred=mean(predicted), sd=sd(predicted)),by=c('emerging')]
  tmp[, variable:=names(carry_forward_model_for_plotting)[mod]]
  return(tmp)
})

outmod=rbindlist(outmod)

pl<-lapply(ordered_vars, function(.var) {
  tmp=outmod[variable==.var]
  ggplot(tmp, aes(x=ifelse(emerging==1, 'developed', 'emerging'), y=meanpred, fill=ifelse(emerging==1, 'developed', 'emerging'))) + 
    theme_bw() + 
    geom_bar(position=position_dodge(), stat="identity") + 
    scale_fill_grey() + 
    labs(title = fig(paste0("", rename.fkt(.var)," elasticity"))) + 
    guides(fill=guide_legend("Development status")) +
    xlab("Development status") + 
    ylab("Elasticity")+ theme(plot.title = element_text(size=10)) +
    geom_errorbar(aes(ymin=meanpred-sd, ymax=meanpred+sd),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))

  })

ggarrange(plotlist=pl, common.legend=TRUE, legend='bottom')


```


```{r randomcombined4, echo = FALSE, results='asis'}

m1 = update.formula(update.formula(form_random_component_FE, form_std), form_extraregressor)

cat("<P style='page-break-before: always'>")
out5=regmodel(formula=m1, dat=elast, model='lmer')
covlabels=unlist(sanitize_table(data.frame(colnames(out5[[1]]$lt[[1]]@pp$X))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')
printout(out5, 'lt', omit=NULL, title = tab('DV: long-term elasticities, with country-fixed effects'),vars=ordered_vars, notes=paste0("Regression of long-term elasticities on country fixed-effects (baseline: Australia), explanatory variables and two random effects for brands and categories. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided signifiance levels reported. Standard errors in parentheses."), covlabels=covlabels)


```

```{r correltabinfra, echo=FALSE, results='asis'}

m1 = update.formula(update.formula(form_random_component_FE, form_std), form_extraregressor)

out5=regmodel(formula=m1, dat=elast, model='lmer')

# collect fixed effects
res=rbindlist(lapply(seq(along=out5), function(x) {
 varname=names(out5)[x]
 coefs=data.frame(coef(summary(out5[[x]]$lt[[1]])))
 coefs$country=gsub('as.factor[(]country[)]', '', rownames(coefs))
 coefs=data.table(coefs)[country%in%unique(elast$country)]
 coefs=rbindlist(list(coefs, data.table(0,0,0,'australia')))
 setnames(coefs, c('fe','se','t','country'))
 return(coefs[, ':=' (se=NULL,t=NULL, varname=varname)])
}))

fixedeffects=dcast(res,country~varname, value.var='fe')

tmp <- merge(fixedeffects, gci, by = c('country'))
tmp[, ':=' (country=NULL)]

out=corstars(as.matrix(tmp))

out=data.frame(corstars(as.matrix(tmp)))
out=out[-c(1:4),c(1:4)]


tmp = out
tmp$variable<-rownames(tmp)
tmp$variable_renamed=sapply(rownames(tmp), rename.fkt, dictionary='renaming_gci.txt')
tmp = tmp[, c('variable', 'variable_renamed', ordered_vars)]
rownames(tmp)<-NULL
colnames(tmp)<-sapply(colnames(tmp), rename.fkt)
colnames(tmp)[3:6]<-paste0(colnames(tmp)[3:6], c(' fixed-effect'))
tmp=data.table(tmp)[grepl('[_]s$', variable)]

filters <- list(c(regex='overall[_]|sub[_]', name='summarized pillars in global competitiveness report'),
                c(regex='gci[_]p[0-9]', name='12 pillars in global competitiveness report'))#,
                #c(regex='gci[_][0-9]', name='individual items in global competitiveness report'))

tableno_fixed = tableno

for (filt in filters) {                
  cat("<P style='page-break-before: always'>")

print(kable(tmp[grepl(filt["regex"], variable),][, variable:=NULL], caption = tab(paste0('Correlations of ', filt["name"], ' (scores) with marketing-mix elasticities')),
      format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(general=paste0('Note: Table reports, for each marketing mix instrument, the correlations between the scores of ', filt["name"], ' (2010/2011 data, see https://www.weforum.org/reports/global-competitiveness-report-2010-2011), and the country-fixed effects reported in Table ', tableno_fixed, '. N = ', nrow(fixedeffects), '. Significance levels: *p<.1, **p<.05, ***p<.01, ****p<.001.')))
}

```

```{r report_pca, echo=FALSE,results='asis'} 

scores = fread('../output/pca_1comp_loadings.csv')
setnames(scores, c('variable', 'stdloading'))

scores[, variable_renamed:=sapply(variable, rename.fkt, dictionary='renaming_gci.txt')]
setcolorder(scores, c('variable_renamed', 'stdloading', 'variable'))
scores[, variable:=NULL]
setnames(scores, 'variable_renamed', 'Variable')
setnames(scores, 'stdloading', 'Standardized loading')

print(kable(scores, caption = tab(paste0('Standardized loadings on principal component for GCI metrics')),
      format='html', initial.zero = FALSE, digits = 3)%>%
        kable_styling())

```


```{r randomcombined_factorscore, echo = FALSE, results='asis'}
m1 = update.formula(form_modelbasis, form_extraregressor)
m1b = update.formula(m1, .~.+gcifactor_mc)

names(ordered_vars) <- paste0(unlist(sanitize_table(data.frame(ordered_vars))), ' elasticity')

out1=regmodel(formula=list(m1b), dat=elast, model='lmer')
carry_forward_model_for_plotting = out1

notes_base = paste0("Regression of long-term elasticities on explanatory variables and three random effects, for brands, categories, and countries, respectively. Estimated using a linear mixed-effects model. ", estimnote, " Two-sided significance levels reported. Standard errors in parentheses.")

cat("<P style='page-break-before: always'>")

covlabels=unlist(sanitize_table(data.frame(unique(unlist(lapply(out1[[1]]$lt, function(x) colnames(x@pp$X)))))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out1, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries, with GCI component score'), vars=ordered_vars,notes=notes_base, covlabels=covlabels,
         column.separate=unlist(lapply(out1, function(x) length(x$lt))))

# interaction model
cat("<P style='page-break-before: always'>")
out4=regmodel(formula=form_interact_gci, dat=elast, model='lmer')

covlabels=unlist(sanitize_table(data.frame(colnames(out4[[1]]$lt[[1]]@pp$X))))
covlabels=c(covlabels[-which(covlabels=='(Intercept)')], 'Constant')

printout(out4, 'lt', omit=NULL, title = tab('DV: long-term elasticities, pooled sample of developed and emerging countries, using interactions with the GCI component score'), vars=ordered_vars, notes=paste0(notes_base), covlabels=covlabels)

```


# Appendix

```{r reset, echo=FALSE,results='asis'}
tableno<<-0
figureno<<-0
cat("<P style='page-break-before: always'>")
  
```


```{r sample_origin, echo=FALSE, results='asis'}

cols =  c('country_of_origin')
tmp = elast[, list(.N), by = c('brand',cols)]
tmp = tmp[, list(nbrands=length(unique(brand)), all_brands=paste(stri_trans_totitle(brand[order(brand)]), collapse=', ')), by = cols]
tmp[country_of_origin==''|is.na(country_of_origin), country_of_origin := 'Country not available']
tmp[, country_of_origin:=my_capitalize(country_of_origin)]

setorderv(tmp, 'nbrands', order=-1L)
setcolorder(tmp, c('country_of_origin', 'nbrands', 'all_brands'))

tmp=sanitize_table(tmp)

kable(tmp, caption = tab('Country-of-origins for brands in sample, ordered by the number of brands from a given country', prefix ='A'),format='html') %>%
        kable_styling() %>% footnote(general=paste0('Note: Brand names listed alphabetically.'))

```





```{r elast_by_win, echo=F,results='asis'}

for (byvar in c('category', 'country')) {
  tmp=elast[!is.na(elastlt), list(elast = sum(elastlt*w_elastlt)/sum(w_elastlt)), by=c('variable', byvar)]
  setnames(tmp, byvar, 'byvar')
  
  tmp=dcast(tmp,byvar~variable,value.var='elast')
  setnames(tmp, 'byvar', byvar)
  setcolorder(tmp, c(byvar, ordered_vars))
  
  tmp=sanitize_table(tmp)
  setorderv(tmp, colnames(tmp)[1])
  
  cat("<P style='page-break-before: always'>")
  print(kable(tmp, digits=3, caption = tab(paste0('Long-term elasticities (by ', byvar, ')'), prefix='A'), format='html', initial.zero = FALSE) %>%
        kable_styling() %>% footnote(general=paste0('Note: ', estimnote, ' Reported by ', ifelse(byvar=='country', 'countries', 'categories'), ' in alphabetical order.')))
}
  
```	


```{r rq4_growth, echo=FALSE,results='asis'}
tmp=unique(elast, by = c('market_id')) # t-tests on growth rates

t_tests <- lapply(unique(elast$category), function(var) {
    tmpdat = tmp[category == var]
    teststat=t.test(tmpdat[country_class=='hinc']$market_growth, tmpdat[country_class=='linc']$market_growth)
    
    tabl = data.frame(category=var, mean1=teststat$estimate[1], mean2=teststat$estimate[2], t=teststat$statistic, p=teststat$p.value)
                
    return(list(summary=tabl))
})

out=rbindlist(lapply(t_tests, function(x) x$summary))

percent <- function(x, digits = 1, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}

out[, ':=' (mean1=percent(mean1-1), mean2=percent(mean2-1))]
out[, category:=as.character(category)]
out=sanitize_table(out)
setorder(out, Category)
setnames(out, 'mean1', 'developed countries')
setnames(out, 'mean2', 'emerging countries')
cat("<P style='page-break-before: always'>")
kable(out, format='html',caption = tab('Average category growth rates for developed and emerging countries',prefix='A'),digits=3) %>% kable_styling() %>% footnote(general=paste0('Note: Table reports average category growth rates, and the results of a t-test of statistical significance of the difference in growth rates between developed and emerging countries. Categories are ordered alphabetically.'))
  
```

```{r VIFS, echo=FALSE,results='asis'}

m1 = ~1+ appliance + ln_market_growth_mc + ln_herf_mc + local_to_market  + ln_overall_prindex_mc 

m<-lm(update(elast~., m1), data=elast[variable=='llen'])

frame1=data.frame(vif(m))
colnames(frame1) <- c('VIF')
frame1$variable=rownames(frame1)
rownames(frame1)<-NULL
frame1=frame1[, c('variable','VIF')]
frame1=sanitize_table(frame1)
cat("<P style='page-break-before: always'>")
kable(frame1,format='html', caption = tab('VIFs in a model without interactions', prefix='A'))%>% kable_styling() %>% footnote(general=paste0('Note: VIFs calculated in regression models using the variables listed above (i.e., excluding brand, category, and country effects).'))

```

```{r elasts_full, echo=F,results='asis'}

cat("<P style='page-break-before: always'>")

  sigvalue = .1 # .1-level of significance
  zval = qnorm(1-sigvalue/2)

  out = lapply(list(st=c('elast', 'z_elast', 'w_elast'), lt = c('elastlt','z_elastlt','w_elastlt')), function(obj) {
               
    tmp = elast[!is.na(get(obj[1]))][, ':=' (val=get(obj[1]), val_z=get(obj[2]), val_w=get(obj[3]))]
    
    tmp=tmp[, list(Neffects=.N, median_elast = median(val), 
												  melast = sum(val*val_w)/sum(val_w),
												  perc_positive = length(which(val_z>=(zval)))/.N, 
												  perc_null = length(which(abs(val_z)<zval))/.N, 
												  perc_negative = length(which(val_z<=(-zval)))/.N), by=c('variable')]
    
  tmp=tmp[match(ordered_vars, variable)]
  setnames(tmp, 'variable', 'mmixinstr')
  return(tmp)
  })
  
iters = list(st=c('st', 'Short-term'), lt=c('lt', 'Long-term'))
for (iter in iters) {
  print(kable(sanitize_table(out[[iter[1]]]), digits=3, format='html', 
        caption=tab(paste0(iter[2], ' elasticities by marketing mix instrument'),prefix='A')) %>% kable_styling() %>% 
        footnote(general=paste0('Note: Table reports ', tolower(iter[2]), ' elasticities. ', estimnote, ' Significance tested at p<',sigvalue, '.')))
}

```

# Estimation details

## Market share attraction model

Elasticities estimated using a market share attraction model (MCI), with

* four marketing mix instruments:
     + llen = line length (number of SKUs)
     + wpswdst = distribution (weighted using past sales in previous three periods)
     + price = rwpspr (deflated using a country's CPI, weighted using past sales in previous three periods)
     + novelty = nov6sh (number of SKUs introduced in past six periods, expressed as a share of total SKUs sold in a given period)
  
* endogeneity controls using Gaussian Copulas (tested at p<.1; removed if n.s.)
* lagged market share to model dynamics
* brand-specific trend
* brand-specific quarterly dummies

Elasticities and corresponding standard errors calculated using the Delta rule.

## Estimation data set

- Number of markets: `r length(unique(elast_all$market_id))`.
- Number of brands: `r nrow(elast_all[, .N, by = c('market_id', 'brand')])`.
- Number of unique brands: `r nrow(elast_all[, .N, by = c('brand')])`.
- Included countries (`r length(unique(elast_all$country))`): `r paste0(unique(elast_all$country),collapse = ', ')`.
- Included categories (`r length(unique(elast_all$category))`): `r paste0(unique(elast_all$category),collapse = ', ')`.

```{r overview2, echo=FALSE, results='asis'}
tmp = elast_all[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
#print(xtable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data')), scalebox='0.6',type='html',caption.placement='top')
tabl=sanitize_table(tabl)
setorder(tabl, Category)
kable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data', prefix='A'))

```


```{r sample_overview, echo=FALSE, results='asis'}
#, headquarter_region=unique(country_of_origin)
tmp=elast[, list(active_in_countries=length(unique(country)), active_in_categories=length(unique(category)), headquarter_location=unique(country_of_origin)), by = c('brand')]
setorderv(tmp, c('active_in_countries','active_in_categories', 'brand'),order=-1L)

tmp[, ':=' (brand=stri_trans_totitle(brand), headquarter_location=stri_trans_totitle(headquarter_location))]#, #headquarter_region=stri_trans_totitle(headquarter_region))]
tmp=sanitize_table(tmp)


kable(tmp, caption = tab('Overview of selected brands, ordered by the number of countries and categories it is active in', prefix ='A'))
```
