---
title: "GfK Singapore"
output:
  html_document
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(data.table)
require(stargazer)
library(knitr)
require(xtable)
require(texreg)
library(sjstats)

options(xtable.comment = FALSE)

# Load results
  load(file = c('../temp/results_20180205.RData'))

# determine model to analyze
  results_brands <- results_MNL
  
# identify model crashes
	checks <- unlist(lapply(results_brands, class))
	table(checks)
	last.item = length(analysis_markets)

# load data
	brand_panel=fread('../temp/preclean.csv')
	brand_panel[, ':=' (date = as.Date(date))]
	
	# elasticities
	elast <- rbindlist(lapply(results_brands[!checks=='try-error'], function(x) x$elast))

	# merge some more variables to it
	vars = c('cat_class', 'country_class')
	tmp = brand_panel[, c('market_id', vars), with=F]
	setkey(tmp, market_id)
	tmp = unique(tmp)
	
	elast = merge(elast, tmp, all.x=T, all.y=F, by = c('market_id'))
	
	
new <- c('tablets', 'phones_smart')

wb_lowermidx = c('india','indonesia', 'vietnam', 'philippines')
wb_uppermidx = c('china', 'malaysia','thailand')


elast[, new:=category%in%new]
elast[, wb_lowermid:=country%in%wb_lowermidx]
elast[, wb_uppermid:=country%in%wb_uppermidx]

elast[, low := wb_lowermid+wb_uppermid]

tableno<<-0
figureno<<-0
fig<-function(caption) {figureno<<-figureno+1;paste0('Figure ', figureno, ': ', caption)}
tab<-function(caption) {tableno<<-tableno+1;paste0('Table ', tableno, ': ', caption)}
```

# Estimation sample
## Overview

Number of markets: `r length(unique(elast$market_id))`.
Number of brands: `r nrow(elast[, .N, by = c('market_id', 'brand')])`.
Number of unique brands: `r nrow(elast[, .N, by = c('brand')])`.

## In how many countries are brands active?

```{r brand_activity, echo=FALSE,results='asis'}
tmp=elast[, list(ncountries=length(unique(country))), by = c('brand')]

hist(tmp$ncountries,main=fig('Distribution of brands that are active in a given number of countries (estimation data)'), xlab='countries',breaks=12,cex.main=.8)
tmp=data.table(table(tmp$ncountries))
setnames(tmp, c('number of countries', 'active brands'))
print(xtable(tmp,caption=tab('Frequency table of brands that are active in a given number of countries (estimation data)')),include.rownames=FALSE,type='html',longtable=T,caption.placement='top')

```

```{r overview2, echo=FALSE, results='asis'}
tmp = elast[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
print(xtable(tabl, caption = tab('Overview of categories and countries (with number of brands indicated for each market), in estimation data')), scalebox='0.6',type='html',caption.placement='top')
```

## Elasticities

### Short-term

```{r elast_overall, echo = FALSE, results='asis'}
.vars=c('llen','wpswdst','rwpspr','nov6sh')
	zval=1.64
	tmp=elast[!is.na(coef), list(median_elast = median(elast), 
												  w_elast = sum(elast/elast_se)/sum(1/elast_se), 
												  N_brands= .N, 
												  perc_positive = length(which(z>=(zval)))/.N, 
												  perc_null = length(which(abs(z)<zval))/.N, 
												  perc_negative = length(which(z<=(-zval)))/.N), by=c('variable')]
	print(xtable(tmp[match(.vars, variable)], caption = tab('Short-term elasticities by variable for all brands (significance tested at p<.1 (z >= 1.64).')),type='html',caption.placement='top')
	

	if(0){# Copulas
	copulas <- rbindlist(lapply(results_brands[!checks=='try-error'], function(x) x$model@coefficients))
	copulas <- copulas[grepl('cop_', varname)]
	
	tmp=copulas[!is.na(coef), list(median = median(coef), 
											  weighted = sum(coef/se)/sum(1/se), 
											  N_brands= .N, 
											  perc_positive = length(which(z>=(zval)))/.N, 
											  perc_null = length(which(abs(z)<zval))/.N, 
											  perc_negative = length(which(z<=(-zval)))/.N), by=c('varname')]

	kable(tmp, caption = 'Copula terms by variable (used for getting an understanding about significance)')
}

```

### Long-term

```{r adf, echo=FALSE,results='asis'}

# extract outcomes of adf tests
.vars=c('llen','wpswdst','rwpspr','nov6sh')
adf <- rbindlist(lapply(results_brands[!checks=='try-error'], function(x) x$adf_sur))
adf[, varname:=sapply(variable, function(x) rev(strsplit(x,'[_]')[[1]])[1])]
# add benchmark brand
adf[, brand2:=sapply(variable, function(x) strsplit(x,'[_]')[[1]][1])]

adf[, y_ur:=ur[variable=='y'], by = c('market_id','brand')]
adf=adf[included==T&varname%in%.vars&!grepl('cop[_]', variable)]

# only retain one brand per market (benchmark kicked out a couple of times)
adf=data.table(adf)

adf[, obs:=.I, by = c('market_id','varname','brand2')]
adf[, isminobs := obs==min(obs), by = c('market_id','varname','brand2')]
adf=adf[isminobs==T]
adf[, obs:=NULL]
adf[, isminobs:=NULL]

adf[, mixed:=!y_ur==ur]

```

#### Elasticities

Long-term elasticities can only be derived for cases in which both variables of a UR, or both variables are stationary. In the results below, mixed cases are removed.

```{r elast_overall_lt, echo = FALSE, results='asis'}
  setkey(adf, market_id, brand2, varname)
  setkey(elast, market_id, brand, variable)
  elast[adf, mixed:=i.mixed]
  
	zval=1.64
	tmp=elast[!is.na(coef)&mixed==F, list(median_elast = median(elastlt), 
												  w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elastlt/elastlt_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elastlt/elastlt_se)<zval))/.N, 
												  perc_negative = length(which(elastlt/elastlt_se<=(-zval)))/.N), by=c('variable')]
	print(xtable(tmp[match(.vars, variable)], caption = tab('Long-term elasticities by variable for all brands (significance tested at p<.1 (z >= 1.64).')),type='html',caption.placement='top')
	
```

#### Outcome of UR tests

Four cases (DV has UR yes/no VS X has UR yes/no). 
Reported as shares (adding up to 1).

```{r urtesting,echo=FALSE, results='asis',warnings=FALSE}

tmp = adf[, list(N=.N), by = c('y_ur','ur','varname')]

for (.var in .vars) {
  printtmp = dcast(tmp[varname==.var], y_ur~ur, value.var='N')[,-1]
  printtmp=printtmp/sum(printtmp)
  rownames(printtmp)<-c('y no UR','y UR')
  colnames(printtmp)<-c('X no UR','X UR')
  
  print(xtable(printtmp,caption=tab(paste0('UR test outcomes: Y vs. ', .var))),include.rownames=T,type='html',caption.placement='top')
}

```


## ANOVAs

### on short-term elasticities
```{r anova_full, echo=FALSE,results='asis', warning=FALSE}
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in .vars) {
  m<-aov(elast~brand+country+category, data=elast, subset=variable==i)
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in FULL sample, short-term'))),type='html',caption.placement='top')
}

```

### on long-term elasticities

```{r anova_full_lt, echo=FALSE,results='asis', warning=FALSE}
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in unique(elast$variable)) {
  m<-aov(elastlt~brand+country+category, data=elast, subset=variable==i)
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in FULL sample, long-term'))),type='html',caption.placement='top')
}

```


# Selected sample
## Overview

```{r brandselect, echo=FALSE,results='asis'}

elast_select = elast[, ncountries:=length(unique(country)), by = c('brand')]
elast_select = elast_select[ncountries>2]
# exclude
elast_select = elast_select[!brand%in% c('unbranded')]

elast_select[, hedon := category %in% c('tablets', 'phones_smart', 'phones_mobile', 'camera_slr', 'camera_compact', 'dvd', 'tv_gen1_crtv', 'tv_gen2_lcd')]
elast_select[, highms := mean_ms>=median(mean_ms), by = c('market_id', 'variable')]

load('..\\..\\derived\\temp\\gdppercap.RData')
gdp = gdppercap[, list(gdppercap=mean(gdppercap,na.rm=T)), by = c('country')]
setkey(gdp, country)
setkey(elast_select, country)
elast_select[gdp, gdppercap:=i.gdppercap]

tmp=elast_select[, list(ncountries=length(unique(country)), ncategories=length(unique(category))), by = c('brand')]
setorderv(tmp, c('ncountries','ncategories'),order=-1L)
print(xtable(tmp, caption=tab('Overview of selected brands (need to be active in at least three countries)')), type='html',caption.placement='top')

```

```{r overview3, echo=FALSE, results='asis'}

tmp = elast_select[, list(Nbrands = length(unique(brand))), by = c('market_id', 'category','country')]

tabl = dcast(tmp, category~country, value.var=c('Nbrands'))
print(xtable(tabl, caption = tab('Overview of included categories and countries (with number of brands indicated for each market), in selected sample')), scalebox='0.6',type='html',caption.placement='top')


```

## Short- and long-term elasticities

```{r elast_selected, echo = FALSE, width = 600,results='asis'}
.vars=c('llen','wpswdst','rwpspr','nov6sh')

	zval=1.64
	tmp=elast_select[!is.na(coef), list(median_elast = median(elast), 
												  w_elast = sum(elast/elast_se)/sum(1/elast_se), 
												  N_brands= .N, 
												  perc_positive = length(which(z>=(zval)))/.N, 
												  perc_null = length(which(abs(z)<zval))/.N, 
												  perc_negative = length(which(z<=(-zval)))/.N), by=c('variable')]
	print(xtable(tmp[match(.vars, variable)], caption = tab('Short-term elasticities by variable in selected sample (significance tested at p<.1 (z >= 1.64).')),type='html',caption.placement='top')
	

	tmp=elast_select[!is.na(coef)&mixed==F, list(median_elast = median(elastlt), 
												  w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se), 
												  N_brands= .N, 
												  perc_positive = length(which(elastlt/elastlt_se>=(zval)))/.N, 
												  perc_null = length(which(abs(elastlt/elastlt_se)<zval))/.N, 
												  perc_negative = length(which(elastlt/elastlt_se<=(-zval)))/.N), by=c('variable')]
	print(xtable(tmp[match(.vars, variable)], caption = tab('Long-term elasticities by variable in selected sample (significance tested at p<.1 (z >= 1.64).')),type='html',caption.placement='top')
		
```

## ANOVAs

### on short-term elasticities
```{r anova, echo=FALSE,results='asis', warning=FALSE}
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in .vars) {
  m<-aov(elast~brand+country+category, data=elast_select, subset=variable==i)
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in SELECTED sample, short-term'))),type='html',caption.placement='top')
}

```


### on long-term elasticities
```{r anova_lt, echo=FALSE,results='asis', warning=FALSE}
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in .vars) {
  m<-aov(elastlt~brand+country+category, data=elast_select, subset=variable==i)
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in SELECTED sample, long-term'))),type='html',caption.placement='top')
}

```

## Plots for short-term elasticities
```{r plots_elast, echo=FALSE, fig.pos="H", include = TRUE,fig.width=12, fig.height=6,dpi=300}

# median elasticities by country
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in .vars) {
  par(mfrow=c(1,3))
  # by country
  tmp_bycntry=elast_select[!is.na(coef)&variable==i, list(w_elast = sum(elast/elast_se)/sum(1/elast_se)), by=c('variable','country')]
	setorderv(tmp_bycntry, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	tmp_bycat=elast_select[!is.na(coef)&variable==i, list(w_elast = sum(elast/elast_se)/sum(1/elast_se)), by=c('variable','category')]
	setorderv(tmp_bycat, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	tmp_bybrand=elast_select[!is.na(coef)&variable==i, list(w_elast = sum(elast/elast_se)/sum(1/elast_se)), by=c('variable','brand')]
	setorderv(tmp_bybrand, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	
	ymin = min(c(tmp_bycntry$w_elast, tmp_bycat$w_elast,tmp_bybrand$w_elast))
	ymax = max(c(tmp_bycntry$w_elast, tmp_bycat$w_elast,tmp_bybrand$w_elast))
	
  cat(paste0('Variable: ', i, '\n'))
  
  barplot(tmp_bycntry$w_elast,names.arg=tmp_bycntry$country, las=2, cex.names=.8, main = fig(paste0(i, ', by countries')),cex.main=.8, ylim = c(ymin, ymax))
	barplot(tmp_bycat$w_elast,names.arg=tmp_bycat$category, las=2, cex.names=.8, main = fig(paste0(i, ', by categories')),cex.main=.8, ylim = c(ymin, ymax))
	barplot(tmp_bybrand$w_elast,names.arg=tmp_bybrand$brand, las=2, cex.names=.8, main = fig(paste0(i, ', by brands')),cex.main=.8, ylim = c(ymin, ymax))
	 }



```

## Plots for long-term elasticities
```{r plots_elast_lt, echo=FALSE, fig.pos="H", include = TRUE,fig.width=12, fig.height=6,dpi=300}

# median elasticities by country
.vars=c('llen','wpswdst','rwpspr','nov6sh')

for (i in .vars) {
  par(mfrow=c(1,3))
  # by country
  tmp_bycntry=elast_select[!is.na(coef)&mixed==F&variable==i, list(w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se)), by=c('variable','country')]
	setorderv(tmp_bycntry, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	tmp_bycat=elast_select[!is.na(coef)&variable==i, list(w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se)), by=c('variable','category')]
	setorderv(tmp_bycat, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	tmp_bybrand=elast_select[!is.na(coef)&variable==i, list(w_elast = sum(elastlt/elastlt_se)/sum(1/elastlt_se)), by=c('variable','brand')]
	setorderv(tmp_bybrand, 'w_elast', ifelse(i=='rwpspr', 1,-1))
	
	ymin = min(c(tmp_bycntry$w_elast, tmp_bycat$w_elast,tmp_bybrand$w_elast))
	ymax = max(c(tmp_bycntry$w_elast, tmp_bycat$w_elast,tmp_bybrand$w_elast))
	
  cat(paste0('Variable: ', i, '\n'))
  
  barplot(tmp_bycntry$w_elast,names.arg=tmp_bycntry$country, las=2, cex.names=.8, main = fig(paste0(i, ', by countries')),cex.main=.8, ylim = c(ymin, ymax))
	barplot(tmp_bycat$w_elast,names.arg=tmp_bycat$category, las=2, cex.names=.8, main = fig(paste0(i, ', by categories')),cex.main=.8, ylim = c(ymin, ymax))
	barplot(tmp_bybrand$w_elast,names.arg=tmp_bybrand$brand, las=2, cex.names=.8, main = fig(paste0(i, ', by brands')),cex.main=.8, ylim = c(ymin, ymax))
	 }

```

## Additional ANOVAs (only for short-term elasticities)
### Emerging vs. developed
Replacing countries by an indicator for high income countries (country_class)

```{r anova2, echo=FALSE,results='asis', warning=FALSE}

for (i in unique(elast_select$variable)) {
  m<-aov(elast~brand+country_class+category, data=elast_select, subset=variable==i)
  #print(anova_stats(m))
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in SELECTED sample, short-term'))),type='html',caption.placement='top')
}

```

### hi/lo economic (country_class), hi/lo brand market share; hi/lo hedonic category
Hi/lo market share: median split on a brand's mean market share, by market
(so, in each market, 50% of the brands are classified as low market share,
and 50% as high market share).

Hedonic categories = tablets, phones, phones, cameras, DVD players, TVs
Utilitarian categories = laptops, desktops, microwave, cooling, washing

```{r anova3, echo=FALSE,results='asis', warning=FALSE}


for (i in unique(elast_select$variable)) {
  m<-aov(elast~highms+country_class+hedon, data=elast_select, subset=variable==i)
  #print(anova_stats(m))
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in SELECTED sample, short-term'))),type='html',caption.placement='top')
}

```
### + interactions

```{r anova4, echo=FALSE,results='asis', warning=FALSE}


for (i in unique(elast_select$variable)) {
  m<-aov(elast~brand+category+country+brand*category+brand*country+category*country, data=elast_select, subset=variable==i)
  #print(anova_stats(m))
  print(xtable(anova_stats(m), caption = tab(paste0("ANOVA for marketing mix ", i, ' in SELECTED sample, short-term'))),type='html',caption.placement='top')
}

```

