---
title: "GfK Singapore - WLS"
output:
  html_document: default
date: "`r format(Sys.time(), '%d %B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
require(stargazer)
library(knitr)
require(xtable)
require(texreg)

options(xtable.comment = FALSE)

# Load data
  elast <- fread('../externals/elast_results_MCI_wlag_wotrend.csv')

# Load auxilary functions
  source('proc_auxilary.R')

# load extra variables
  hdi <- fread('../temp/hdi.csv')
# change taiwan (reported value from China is not reliable)
  hdi[, hdi2010:=ifelse(country=='taiwan', mean(hdi2010[country%in%c('thailand', 'china')]), hdi2010)]
# Load GDP
  gdp <- fread('../temp/gdp.csv')
# Merge
  setkey(hdi, country)
  setkey(elast, country)
  elast[hdi, hdi2010:=i.hdi2010]
  setkey(gdp, country)
  elast[gdp, gdppercap2010:=i.gdppercap2010]


# take natural log of variables
for (var in c('herf','c3','c5','market_growth','hdi2010','gdppercap2010', 'ncat_in_country', 'ncountry_in_category')) {
  elast[, (paste0('ln_', var)):=log(get(var))]
  
}

# focal dummies: local_to_market, western (versus asian)

#
elast[, worldbank := '']
elast[country%in%c('india','indonesia', 'vietnam', 'philippines'), worldbank:='lowermid']
elast[country%in%c('china', 'malaysia','thailand'), worldbank:='uppermid']
elast[worldbank=='', worldbank:='high']


### keep global brands, >2 countries >3 countries
elast=elast[globalbrand==T]
#elast=elast[ncountries>=2]


```

all analyses conducted with WLS, whereby weights correspond to inverse standard errors of estimated short- or long-term elasticities. no clustered SEs used (yet).

# sample overview

```{r sample_overview, echo=FALSE, results='asis'}

tmp=elast[, list(ncountries=length(unique(country)), ncategories=length(unique(category))), by = c('brand')]
setorderv(tmp, c('ncountries','ncategories'),order=-1L)
print(xtable(tmp, caption=tab('Overview of selected brands (need to be active in at least three countries)')), type='html',caption.placement='top')

```

# degree of development

- GDP per capita in 2010
- Human Development Index in 2010 (imputed for Taiwan as mean of China and Thailand)

```{r devel, echo = FALSE}
tmp=unique(elast, by='country')[, c('country','gdppercap2010','hdi2010'),with=F]
setorderv(tmp, c('gdppercap2010'), order=-1L)
kable(tmp, caption=tab('Development indicators for countries in sample'))
```

# investigate emerging country variable

## continuous, log GDP per cap

```{r rq1_regs, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap2010 + as.factor(category) + as.factor(brand), 
                     dat=elast)

, mc = ~ln_gdppercap)

# build mean center feature

printres(out, omit='brand|category')


# log of variables
for (var in c('herf','c3','c5','market_growth','hdi2010','gdppercap2010', 'ncat_in_country', 'ncountry_in_category')) {
  elast[, (paste0('ln_', var)):=log(get(var))]
  
}

# dummies
# local_to_market
# western (versus asian)



```

## HDIxxx

## 2 classes: Taiwan as high-income

```{r rq2, echo = FALSE}
tmp=elast[, list(.N, gdp_per_cap=mean(gdppercap)), by = c('country_class','country')][, N:=NULL]
#print(tmp)
setorderv(tmp, 'gdp_per_cap', order=-1L)
kable(tmp, caption=tab('Country classification: IMF'))
```

```{r twoclasses, echo = FALSE, results='asis'}

out=regmodel(formula=~1+I(country_class=='linc') + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 2 classes: Taiwan as low-income

```{r twoclasses2, echo = FALSE, results='asis'}
elast[,linc_recode:=ifelse(country_class=='linc'|country=='taiwan', 1,0)]

out=regmodel(formula=~1+linc_recode + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```


## 3 classes by worldbank

```{r rq2bb, echo = FALSE}
tmp=elast[, list(.N, gdp_per_cap=mean(gdppercap)), by = c('worldbank','country')][, N:=NULL]
#print(tmp)
setorderv(tmp, 'gdp_per_cap', order=-1L)
kable(tmp, caption=tab('Country classification: Worldbank'))
```

```{r threeclass, echo = FALSE, results='asis'}

out=regmodel(formula=~1+worldbank + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 3 classes by worldbank, with Taiwan as lowermid instead of high
```{r threeclass2, echo = FALSE, results='asis'}
elast[, worldbank_recode:=worldbank]
elast[country=='taiwan', worldbank_recode:='uppermid']

out=regmodel(formula=~1+worldbank_recode + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```


# interaction analysis (continuing with log GDP)

Note: interaction terms indicated with : instead of *.

## 1a. country of origin (four groups)

Displays unique brands (summing to 53) and corresponding country-of-origin categories.

Read: 33 unique brands are either classified as asian other or local. 4 are exclusively classified as asian other, etc.

```{r cootable, echo = FALSE}
tmp=elast[globalbrand==T, list(coo=paste0(unique(country_of_origin)[order(unique(country_of_origin))], collapse=', ')), by = c('brand')][, list(N_brands=.N), by = c('coo')]
kable(tmp, caption=tab('Unique brand/country of origin combinations'))
```

Baseline is asia other.

```{r r1a, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*country_of_origin + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 1b. country of origin (three groups)

combined north america and europe.
baseline is asia other.

```{r r1b, echo = FALSE, results='asis'}
elast[,coo_recoded := country_of_origin]

elast[coo_recoded%in%c('europe', 'northamerica'), coo_recoded:='eur_northameric']

out=regmodel(formula=~1+ln_gdppercap*coo_recoded + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 2. cross-country presence

X = number of unique countries a brand is active in.

```{r r2, echo = FALSE, results='asis'}
out=regmodel(formula=~1+ln_gdppercap*ncountries + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```
## 3. within-country representation

X = number of categories a brand is active in a focal country.

```{r r3, echo = FALSE, results='asis'}
out=regmodel(formula=~1+ln_gdppercap*ncat_in_country + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 4. market share in category

X = market share of focal brand in market (over all years, summing to 1 over all brands).

```{r r4ms, echo = FALSE, results='asis'}
elast[, lnms := log(100*overall_ms)]
out=regmodel(formula=~1+ln_gdppercap*lnms + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 5. growth rate

X = log of growth rate (e.g., .8, 1.03), not multiplied by 100 before logging

```{r r5growth, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*log(market_growth) + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

## 6. concentration

### 6a. Herfindahl

Herfindahl is between 0 and 1.

```{r r5aherf, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*herf + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

### 6b. C3

C3 scaled between 0 and 100. Logged.

```{r r4ac3, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*log(c3*100) + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

### 6c. C5

C5 scaled between 0 and 100. Logged.

```{r r4ac5, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*log(c5*100) + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

### 7. Necessity

X = Necessity dummy, equaling 1 for washing, microwave and cooling.

```{r r7, echo = FALSE, results='asis'}

out=regmodel(formula=~1+ln_gdppercap*necessity + as.factor(category) + as.factor(brand), 
                     dat=elast)

printout(out, 'st', omit='brand|category', title = tab('short-term'))
printout(out, 'lt', omit='brand|category', title = tab('long-term'))

```

